---
title: "Final GNG RT analyses"
subtitle:  "PD Inhibition Project"
author: "Alison Schreiber, Nate Hall"
date: "5/5/2020"
output:
  html_document:
    code_folding: show
    df_print: default
    mathjax: default
    number_sections: no
    theme: spacelab
    toc: yes
    toc_depth: 2
    toc_float: yes
    fig_width: 9 
    fig_height: 6 
  pdf_document:
    code_folding: hide
    df_print: default
    number_sections: no
    toc: yes
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
if (!require(pacman)) { install.packages("pacman"); library(pacman) }
p_load(car, brms, nlme, lme4, loo, readr, tidyverse, emmeans, cowplot, glmmTMB, bbmle, broom)
p_load(car, nlme, lme4, readr, tidyverse, emmeans, cowplot, bbmle, broom, knitr, kableExtra, flextable, stargazer, lmerTest)
knitr::opts_chunk$set(echo = TRUE) #print code by default
#knitr::opts_chunk$set(cache.path = "../../Outputs/flanker_mlms/")
options(digits=3)
options(width = 140)
```

# Load data
Data has already been cleaned and initial analyses completed by NH. 
For RT analyses, use variable rt_log_trim_grp
For outcome analyses, use response -> this indicates whether they correctly Go vs No Go'd (can figure out whether they pressed space or not based on the stim)
Cond refers to number of prior go trials 
Stim refers whether go or no go trial
Use trial_z rather than trial (for scaling purposes)
Will likely add in prev_rt in more complex analyses

N.B. 6/22/20: Nate is going through alison's analyses and converting to lme4 for consistency. This shouldn't change things much. 
Update: I changed things a decent amount. Oops. 


```{r}
#raw flanker data, all subjects. With MNH/NTH recoding of since_nogo as block_trial_z
gng <- read.csv("~/github_dirs/PD_Inhibition_DDM/Data/preprocessed/go_nogo_clean_sample_accCode_recode_sincenogo.csv") 

gng <- mutate(gng, block_trial_z = since_nogo_z)

#set onego to reference 
gng <- mutate(gng, cond = factor(cond, levels = c("OneGo", "ThreeGo", "FiveGo", "SevenGo")))

gng_rt <- dplyr::filter(gng, stim == "Go", response == 1) #only analyze GO RTs!


# test(emtrends(m19, ~trial_z, var = "block_trial_z", at = list(trial_z = c(-1, 1))))
# quantile(gng_rt$prev_rt, .16, na.rm = TRUE) # to get what is equivalent to -1, 1 in z scores
# quantile(gng_rt$prev_rt, .84, na.rm = TRUE)



render_aictab <- function(minfo, ...) {
  mc <- match.call(expand.dots = TRUE)
  mlist <- list(...)
  
  #N.B. AICtab fails if you try to assign names to the list names(mlist) <- ...
  mnames <- sapply(3:length(mc), function(x) { as.character(mc[[x]])})
  mdf <- do.call(rbind, minfo) %>% as.data.frame() %>% rownames_to_column("model")
  adf <- AICtab(mlist, sort=FALSE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE, mnames=mnames) %>% 
    as.data.frame() %>% rownames_to_column("model") %>% dplyr::select(-dLogLik)
  
  res <- mdf %>% left_join(adf, by="model")
  return(res)
}

flextb_vif <- function(m) {
  flextable(data.frame(vif=car::vif(m)) %>% rownames_to_column("Predictor")) %>% autofit()
}

check_singularity <- function(lmerobj) {
  tt <- getME(lmerobj,"theta") #RE estimates
  ll <- getME(lmerobj,"lower") #lower bound on estimate
  
  #look for RE estimates that are very small (near zero) and the lower bound encompasses 0
  low_re <- tt[ll==0 & tt < 1e-2]
  return(low_re)
  
  #eventually, would be nice to provide functionality to drop these from model and refit automatically
}

minfo <- list() #used for building model summary table

```


# RT analyses (from AMS, NTH does things differently (perhaps in part due to not fitting fixed effects covariance structures for simplicity))

1) test Trial and condition + 1|Subject
2) keep fixed  + 1|subject/condition
3) test whether trial as random slope for subject/condition
4) test whether trial as random slope for subject
5) trial*condtion in fixed effects; slope of trial | subject; 1|subject/condition
6) trial*block trial; trial | subject; 1|subject/condition
7) trial*block trial; block trial | subject; 1|subject/condition
8) trial + cond + block trial;trial + 1|subject/condition
9) trial + block trial;trial + 1|subject/condition
10) trial*block trial;trial + 1|subject/condition
11) trial*block trial;trial + block trial + 1|subject/condition
12) trial*block trial;trial + 1 | subject/condition; block trial|subject
13) trial*block trial;trial + 1 | subject/condition;trial|subject
14) trial*block trial;trial + block trial + cond 1 | subject
Compared to earlier iterations not including prev RT, as discussed with NH

## m1: random intercept of subject, fixed = just condition

```{r m1, cache=TRUE}
# m1 <- lme(rt_log_trim_grp ~ trial_z + cond, random = ~ 1 | id,
#           correlation=corCompSymm(form=~trial|id), na.action = na.exclude, 
#           data = gng_rt, method='ML')
# 
# summary(m1)
# emmeans(m1, ~cond)

minfo[["m1"]] <- c(fixed="Trial and Condition", l2="Subject: Intercept")

m1 <- lmer(rt_log_trim_grp ~ trial_z + cond + (1 | id),
           na.action = na.exclude, 
          data = gng_rt)
summary(m1)


m1_reml <- update(m1, REML=TRUE)
emmeans(m1_reml, ~cond)
```

## m2: keep fixed  + 1|subject/condition

```{r m2, cache=TRUE}


minfo[["m2"]] <- c(fixed="Condition and Trial", l2="Subject/Condition: Intercept")

m2 <- lmer(rt_log_trim_grp ~ cond + trial_z+  (1 | id/cond),
           na.action = na.exclude, 
          data = gng_rt)
summary(m2)
```

## m3: test whether trial as random slope for subject/condition

```{r m3, cache=TRUE}

minfo[["m3"]] <- c(fixed="Condition, Trial", l2="Subject/Condition: Intercept, Trial")

m3 <- lmer(rt_log_trim_grp ~ cond + trial_z + (1 + trial_z | id/cond),
           na.action = na.exclude, 
          data = gng_rt)
summary(m3)
```


## m4: test whether trial as random slope for subject

```{r m4, cache=TRUE}
minfo[["m4"]] <- c(fixed="Condition and Trial", l2="Subject: Intercept, Trial")

m4 <- lmer(rt_log_trim_grp ~ cond + trial_z + (1 + trial_z | id),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4))) #bump up iterations)
summary(m4)

```

## m5: trial*condtion in fixed effects; slope of trial | subject; 1|subject/condition

```{r m5, cache = TRUE}
minfo[["m5"]] <- c(fixed="Trials by Condition", l2="Subject: Trial; Subject/Condition: Intercept")

m5 <- lmer(rt_log_trim_grp ~  cond*trial_z + (0 + trial_z | id) + (1 | id/cond),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4))) #bump up iterations)
summary(m5)
```

## m6: trial*block trial; trial | subject; 1|subject/condition

```{r m6, cache=TRUE}
minfo[["m6"]] <- c(fixed="Trials*block trial", l2="Subject: Intercept + Trial; Subject/Condition: Intercept")

m6 <- lmer(rt_log_trim_grp ~  trial_z*block_trial_z + (1 + trial_z| id) + (1 | id/cond),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m6)
```

## m7: trial*block trial; block trial | subject; 1|subject/condition

```{r m7, cache=TRUE}
minfo[["m7"]] <- c(fixed="Trial by Block Trial", l2="Subject: Block Trial; Subject/Condition: Intercept")

m7 <- lmer(rt_log_trim_grp ~  trial_z*block_trial_z + (1 + block_trial_z | id) + (1|id/cond),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m7)
```
## m8: trial + cond + block trial;trial + 1|subject/condition

```{r m8, cache=TRUE}
minfo[["m8"]] <- c(fixed="Trial by Cond by Block Trial", l2="Subject/Cond: Intercept, Trials")

m8 <- lmer(rt_log_trim_grp ~  block_trial_z+trial_z + cond +(1 + trial_z | id),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m8)
```

## m9: trial + block trial;trial + 1|subject/condition

```{r m9, cache=TRUE}
minfo[["m9"]] <- c(fixed="Block Trial, Trial number", l2="Subject/Condition: Intercept, Trials")

m9 <- lmer(rt_log_trim_grp ~  block_trial_z + trial_z + (1 + trial_z | id/cond),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m9)
```


## m10: trial*block trial;trial + 1|subject/condition

```{r m10, cache=TRUE}
minfo[["m10"]] <- c(fixed="Trials from no-go by Trial number", l2="Subject/Condition: Intercept, Trials")

m10 <- lmer(rt_log_trim_grp ~  block_trial_z*trial_z + (1 + trial_z| id/cond),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m10)
```


## m11: trial*block trial;trial + block trial + 1|subject/condition

```{r m11, cache=TRUE}
minfo[["m11"]] <- c(fixed="Trials from no-go by Trial number", l2="Subject/Cond: Intercept, Trials from no-go, Trial")

m11 <- lmer(rt_log_trim_grp ~  block_trial_z*trial_z + (1 + block_trial_z + trial_z| id/cond),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m11)
```


## m12: trial*block trial;trial + 1 | subject/condition; block trial|subject

```{r m12, cache=TRUE}
minfo[["m12"]] <- c(fixed="Trials from no-go by Trial", l2="Subject/Cond: Trials, Intercept; Subject: Trials from no-go")

m12 <- lmer(rt_log_trim_grp ~  block_trial_z*trial_z + (1 + block_trial_z| id) + (1 + trial_z | id/cond),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m12)
```


## m13: trial*block trial;block_trial + 1 | subject/condition;trial|subject

```{r m13, cache=TRUE}
minfo[["m13"]] <- c(fixed="Trials from no-go, Trial number, Trials from no-go x Trial number", 
                    l2="Condition within subject: Trials \nSubject: Intercept, Trial")

m13 <- lmer(rt_log_trim_grp ~  block_trial_z*trial_z + (1 + trial_z| id) + (1 + block_trial_z | id/cond),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m13)

```

## m14: trial*block trial;trial + block trial + cond 1 | subject

```{r m14, cache=TRUE}
minfo[["m14"]] <- c(fixed="Trials from no-go, Trial number, Trials from no-go x Trial number", 
                    l2="Subject: Trial + Block Trial + Cond + Intercept")

m14 <- lmer(rt_log_trim_grp ~  block_trial_z*trial_z + (1 + block_trial_z + trial_z + cond | id),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m14)
# emmeans(m2, ~cond)

AICtab(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12, m13, m14, sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 

```

#m15: add in prev error into fixed effects
m12 currently best
trial*block trial;trial + 1 | subject/condition; block trial|subject

```{r}
minfo[["m15"]] <- c(fixed="Trials from no-go by Trial, Prev Error", l2="Subject/Cond: Trials, Intercept; Subject: Trials from no-go")

m15 <- lmer(rt_log_trim_grp ~  block_trial_z*trial_z + prev_error + (1 + block_trial_z| id) + (1 + trial_z | id/cond),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m15)

```
m15 obs: 19074
m12 obs: 19244 > Thus cannot compare the two. 
prev_error sig so continue with adding it. 
#m16: see if prev error inter acts with other effects

```{r}
minfo[["m16"]] <- c(fixed="Trials from no-go by Trial by Prev Error", l2="Subject/Cond: Trials, Intercept; Subject: Trials from no-go")

m16 <- lmer(rt_log_trim_grp ~  block_trial_z*trial_z*prev_error + (1 + block_trial_z| id) + (1 + trial_z | id/cond),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m16)
anova(m16) # see if a subset of interactions sig

```

#m17: see if prev error interacts with block trial z

```{r}
minfo[["m17"]] <- c(fixed="Trials from no-go by Trial by Prev Error", l2="Subject/Cond: Trials, Intercept; Subject: Trials from no-go")

m17 <- lmer(rt_log_trim_grp ~  block_trial_z*trial_z+ block_trial_z*prev_error + (1 + block_trial_z| id) + (1 + trial_z | id/cond),
           na.action = na.exclude, 
          data = gng_rt, control=lmerControl(optCtrl=list(maxfun=2e4)), REML = FALSE) #bump up iterations)
summary(m17)
anova(m17) # see if a subset of interactions sig
AICtab(m15, m16, m17, sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 
# most evidence for there being an interaction. 
```