---
title: "Final GNG Accuracy Analyses"
subtitle:  "PD Inhibition Project"
author: "Nate Hall, Alison Schreiber"
date: "5/5/2020"
output:
  html_document:
    code_folding: show
    df_print: default
    mathjax: default
    number_sections: no
    theme: spacelab
    toc: yes
    toc_depth: 2
    toc_float: yes
    fig_width: 9 
    fig_height: 6 
  pdf_document:
    code_folding: hide
    df_print: default
    number_sections: no
    toc: yes
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---
```{r setup, include=FALSE}
if (!require(pacman)) { install.packages("pacman"); library(pacman) }
p_load(car, brms, nlme, lme4, loo, readr, tidyverse, emmeans, cowplot, glmmTMB, bbmle, broom)
p_load(car, nlme, lme4, readr, tidyverse, emmeans, cowplot, bbmle, broom, knitr, kableExtra, flextable, stargazer, lmerTest)
knitr::opts_chunk$set(echo = TRUE) #print code by default
#knitr::opts_chunk$set(cache.path = "../../Outputs/flanker_mlms/")
options(digits=3)
options(width = 140)
```

# Load data
Data has already been cleaned and initial analyses completed by NH. 
For RT analyses, use variable rt_log_trim_grp
For outcome analyses, use response -> this indicates whether they correctly Go vs No Go'd (can figure out whether they pressed space or not based on the stim)
Cond refers to number of prior go trials 
Stim refers whether go or no go trial
Use trial_z rather than trial (for scaling purposes)
Will likely add in prev_rt in more complex analyses


```{r}
gng <- read.csv("~/github_dirs/PD_Inhibition_DDM/Data/preprocessed/go_nogo_clean_sample_accCode_recode_sincenogo.csv") %>% mutate(bad_subj = if_else(subj_idx == 15, 1, 0)) #flagged 15 as bad as this was the one person who needed to be according to NH's preprocessing; will test how inclusion of 15 alters results
gng <- mutate(gng, cond= factor(cond, levels = c("OneGo","ThreeGo", "FiveGo", "SevenGo")))

gng <- gng %>% group_by(subj_idx) %>% mutate(
  
                                      prev_rt = ifelse(lag(rt_log_trim_grp) == 0, NA, lag(rt_log_trim_grp)),
                                      
                                      prev_rt_z = scale(prev_rt),
                                      prev_error = ifelse(lag(response) == 1, 0, 1),
                                      id = as.character(subj_idx))


# gng_rt <- dplyr::filter(gng, stim == "Go", response == 1) #only analyze GO RTs!
# gng_rt$cond_id <- with(gng_rt, interaction(cond,id))
gng <- mutate(gng, block_trial_z = since_nogo_z)


# test(emtrends(m19, ~trial_z, var = "block_trial_z", at = list(trial_z = c(-1, 1))))
# quantile(gng_rt$prev_rt, .16, na.rm = TRUE) # to get what is equivalent to -1, 1 in z scores
# quantile(gng_rt$prev_rt, .84, na.rm = TRUE)

# unique(gng_rt$bad_subj)

render_aictab <- function(minfo, ...) {
  mc <- match.call(expand.dots = TRUE)
  mlist <- list(...)
  
  #N.B. AICtab fails if you try to assign names to the list names(mlist) <- ...
  mnames <- sapply(3:length(mc), function(x) { as.character(mc[[x]])})
  mdf <- do.call(rbind, minfo) %>% as.data.frame() %>% rownames_to_column("model")
  adf <- AICtab(mlist, sort=FALSE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE, mnames=mnames) %>% 
    as.data.frame() %>% rownames_to_column("model") %>% dplyr::select(-dLogLik)
  
  res <- mdf %>% left_join(adf, by="model")
  return(res)
}

flextb_vif <- function(m) {
  flextable(data.frame(vif=car::vif(m)) %>% rownames_to_column("Predictor")) %>% autofit()
}

check_singularity <- function(lmerobj) {
  tt <- getME(lmerobj,"theta") #RE estimates
  ll <- getME(lmerobj,"lower") #lower bound on estimate
  
  #look for RE estimates that are very small (near zero) and the lower bound encompasses 0
  low_re <- tt[ll==0 & tt < 1e-2]
  return(low_re)
  
  #eventually, would be nice to provide functionality to drop these from model and refit automatically
}

minfo <- list() #used for building model summary table

```


# Resp analyses
Here, were are predicted whether individuals Go versus No-Go'd.
Relevant aspects of the model: stimuli (whether Go vs. No Go), condition, block trial and trial
Will initially test a model of trial, stim and cond as fixed effects and will then add block trial. Finally, I will add in random slopes to the random effects structure and will then ensure that the preferred model is as simple as it can be. 

```{r}
gng <- mutate(gng, go = if_else((response == 1 & stim == "Go" )|(response == 0 & stim == "NoGo"), 1, 0))
str(gng)
```


# Resp analyses
Here, were are predicted whether individuals Go versus No-Go'd.
Relevant aspects of the model: stimuli (whether Go vs. No Go), condition, block trial and trial
Will initially test a model of trial, stim and cond as fixed effects and will then add block trial. Finally, I will add in random slopes to the random effects structure and will then ensure that the preferred model is as simple as it can be. 

```{r}
gng <- mutate(gng, go = if_else((response == 1 & stim == "Go" )|(response == 0 & stim == "NoGo"), 1, 0))

```

## m25 tests interaction between stim and cond
starting point in ML: random intercept of subject, compound symmetry residual correlation structure wrt trial

```{r m25, cache=TRUE}
m25 <- glmer(response ~ trial_z + cond*stim + (1 | subj_idx), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m25)
emmeans(m25, ~cond)
```

## m26 tests whether additive effects of trial, cond and stim
Much preferred to have cond and stim not interact

```{r m26, cache=TRUE}
m26 <- glmer(response ~ trial_z + cond + stim + (1 | subj_idx), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m26)
emmeans(m26, ~cond)
AICtab(m25, m26,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```

## m27 tests whether two way interaction for trial and cond
Does trial interact with cond? Nope
```{r m27, cache=TRUE}
m27 <- glmer(response ~ trial_z*cond + stim + (1 | subj_idx), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m27)
emmeans(m27, ~cond)
AICtab(m27, m26,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```

## m28 sees whetehr two-way interaction for trial and stim
Does trial interact with stim? Support for an interaction and m28 preferred (83%).
```{r m28, cache=TRUE}
m28 <- glmer(response ~ trial_z*stim + cond + (1 | subj_idx), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m28)
emmeans(m28, ~cond)
AICtab(m28, m26,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```

## m29 tests whether there is a three way interaction between trial stim and cond
Double check that not a three way interaction? Nope. 
```{r m29, cache=TRUE}
m29 <- glmer(response ~ trial_z*stim*cond + (1 | subj_idx), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m29)
emmeans(m29, ~cond)
AICtab(m28, m29,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```

## m30 tests what the addititve value of including both block trial and cond is 
Building on m28, add in block trial. No evidence for block trial and the simpler m28 preferred. 
```{r m30, cache=TRUE}
m30 <- glmer(response ~ trial_z*stim + cond + block_trial_z + (1 | subj_idx), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m30)
emmeans(m30, ~cond)
AICtab(m28, m30,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```

## m31 tests whether block trial can replace cond (as that would be simpler)
Building on m30, add in block trial. See whether block trial is redundant with cond by excluding cond.
While block trial becomes non-significiant, AIC strongly favors m28 over m31. Based off of this, will instead focus on cond rather than block trial. 
```{r m31, cache=TRUE}
m31 <- glmer(response ~ trial_z*stim + block_trial_z + (1 | subj_idx), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m31)
AICtab(m28, m31,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```

## m32 tests whether random slope of each cond with each subject helps
Check whether a different intercept structure makes sense. Not strong evidence for including cond as part of the nesting structure. 
```{r m32, cache=TRUE}
m32 <- glmer(response ~ trial_z*stim + cond + (1 | subj_idx/cond), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m32)
emmeans(m32, ~cond)
AICtab(m28, m32,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```

## m33 tests whether random intercepts estimated per stimuli per subject helps
Check whether a different intercept structure makes sense. Super strong evidence in favor of having stim be part of the nesting structure for random intercepts. 
```{r m33, cache=TRUE}
m33 <- glmer(response ~ trial_z*stim + cond + (1 | subj_idx/stim), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m33)
emmeans(m33, ~cond)
AICtab(m28, m33,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```


## m34 tests whether random slope of cond helps
See whether cond belong as a random slope.That's a no. 
```{r m34, cache=TRUE}
m34 <- glmer(response ~ trial_z*stim + cond + (1 + cond | subj_idx/stim), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m34)
emmeans(m34, ~cond)
AICtab(m34, m33,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```

## m35 tests whether random slope of stim for each stim within each subject helps  
See whether can have stim as a random slope
```{r m35, cache=TRUE}
m35 <- glmer(response ~ trial_z*stim + cond + (1 + stim| subj_idx/stim), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m35)
emmeans(m35, ~cond)
AICtab(m35, m33,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```
m31: Obs: 24621 and m36 obs is 24621 > Thus can actually take to heart that trials form go is not important predictor. 

## FAVORITE! m36 tests ranodm slope esimated for stimuli for each subject
See whether can have stim as a random slope. 36 is slightly preferred and is simpler. 
```{r m36, cache=TRUE}
m36 <- glmer(response ~ trial_z*stim + cond + (1 | subj_idx:stim) + (1 + stim | subj_idx), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m36)
emmeans(m36, ~cond)
AICtab(m35, m36,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 
AICtab(m25, m26, m27, m28, m29, m30, m31, m32, m33, m34, m35, m36,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```

## m37 sees whether random slopes for trial estimated per subject helps
See whether can have stim as a random slope. 36 is slightly preferred and is simpler. 
```{r m37, cache=TRUE}
m37 <- glmer(response ~ trial_z*stim + cond + (1 | subj_idx:stim) + (1 + stim + trial_z | subj_idx), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m37)
emmeans(m37, ~cond)
AICtab(m37, m36,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```



## m38 tests whether if random slopes for trial estimated per stimuli per subject helps 
36 still strongly preferred
```{r m38, cache=TRUE}
m38 <- glmer(response ~ trial_z*stim + cond + (1 + trial_z | subj_idx:stim) + (1 + stim + trial_z | subj_idx), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m38)
emmeans(m38, ~cond)
AICtab(m36, m38,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```

## m39 tests whether can simplify by only including stim as random slope
Testing if I can make 36 simpler by only including stim in random slopes. Does not help. 36 highly preferred. 
```{r m39, cache=TRUE}
m39 <- glmer(response ~ trial_z + cond + (1 | subj_idx:stim) + (1 + stim | subj_idx), na.action = na.exclude, 
          data = gng, family = "binomial",nAGQ=0,
      control=glmerControl(optimizer = "nloptwrap"))

summary(m39)
emmeans(m39, ~cond)
AICtab(m39, m36,sort=TRUE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE) 


```

Thus, m36 is the winner. 

