---
title: "FlankerMLMs"
author: "Nate Hall"
date: "2/20/2020"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#specify that chunks should run relative to the root working directory (may need to be changed per user)
knitr::opts_knit$set(root.dir = "/Users/nth7/PD_Inhibition_DDM")

# setwd("~/PD_Inhibition_DDM")

#load necessary packages
if (!require(easypackages)) { install.packages("easypackages"); library(easypackages) }
packages("ggplot2", "dplyr", "tidyr", "sas7bdat", "psych", "cowplot", "beepr", "retimes", "lme4", "MuMIn", "jtools", "lmerTest", "interactions")
```

## Basic multilevel modeling of flanker data

Once these steps are complete, use `lme4::lmer` and `lme4::glmer` to model RTs and accuracies, respectively. The model will contain a random intercept per subject `(1 | Subject)` reflecting trials nested within subject. There may be fixed or random linear effects of trial, which would reflect gradual speeding or slowing of RTs or improvement/degradation of accuracy. Residual covariance structures such as AR(1) or compound symmetry may also be considered using the `nlme::lme` function. Something like:

```{r tidy=FALSE, eval=FALSE}
lme(RT ~ trial + Incongruent*CongruentBlock, random = ~ 1 | Subject,
    correlation=corCompSymm(form=~trial|person), na.action = na.exclude, 
    data = flanker,method='REML'))
```

Use likelihood ratio tests (typically `anova` on `lmer` objects) to adjudicate best fit.

Start NH simple RT modelling in lmer

```{r NH MLM}

load("Data/preprocessed/flank_use.RData")

# flank_use <- flank_use %>% left_join(SNAPt, by = "Subject")

m1 <- lmer(rt ~ Incongruent + (1|Subject), data = flank_use)
m2 <- lmer(rt ~ CongruentBlock + (1|Subject), data = flank_use)
m3 <- lmer(rt ~ CongruentBlock*Incongruent + (1|Subject), data = flank_use)

MuMIn::AICc(m1,m2,m3)
vif.lme(m3) #looks good, no concerns around collinearity
# summ(m3)

m4 <- lmer(rt ~ CongruentBlock*Incongruent + prev_stim + (1|Subject), data = flank_use)
m5 <- lmer(rt ~ CongruentBlock*Incongruent + trial_block + (1|Subject), data = flank_use)
m6 <- lmer(rt ~ CongruentBlock*Incongruent + trial_sub + (1|Subject), data = flank_use)
MuMIn::AICc(m3,m4,m5,m6)
vif.lme(m5) #still good
summ(m5)

m7 <- lmer(rt ~ CongruentBlock*Incongruent * prev_stim + (1|Subject), data = flank_use)
m8 <- lmer(rt ~ CongruentBlock*Incongruent * trial_block + (1|Subject), data = flank_use)
m9 <- lmer(rt ~ CongruentBlock*Incongruent * trial_sub + (1|Subject), data = flank_use)
MuMIn::AICc(m5,m7,m8, m9)
vif.lme(m8) # this is more concerning, probabaly best to fall back on the simpler m5.
# summ(m8)

```



```{r add SNAP dims}
cor_heatmap(flank_use)

for(dim in names(select(flank_use, contains("Z_")))){
  print(dim)
  #specify candidate models
  f1 <- formula(paste0("rt ~ CongruentBlock*Incongruent + trial_block + ",dim ," + (1|Subject)"))
  f2 <- formula(paste0("rt ~ CongruentBlock*Incongruent*",dim, " + trial_block + (1|Subject)"))
  f3 <- formula(paste0("rt ~ CongruentBlock*Incongruent + ",dim, "*Incongruent + trial_block + (1|Subject)"))
  f4 <- formula(paste0("rt ~ CongruentBlock*Incongruent + ",dim, "*CongruentBlock + trial_block + (1|Subject)"))
  
  
  #run candidate models
  mod_lists <- list()
  mod_lists[["m10"]] <- lmer(formula = f1, data = flank_use)
  mod_lists[["m11"]] <- lmer(formula = f2, data = flank_use)
  mod_lists[["m12"]] <- lmer(formula = f3, data = flank_use)
  mod_lists[["m13"]] <- lmer(formula = f4, data = flank_use)
  
  
  #perform model comparison
  aics <- MuMIn::AICc(m5, mod_lists[["m10"]], mod_lists[["m11"]], mod_lists[["m12"]], mod_lists[["m13"]])%>% rownames_to_column() %>% arrange(AICc)
  aics[,1] <- do.call(rbind,lapply(aics$rowname, function(x)paste0("m",gsub("[^0-9.-]", "", x))))
  
  print(aics)
  
  winmod <- aics[1,"rowname"]
  
  # m5aic <- MuMIn::AICc(m5)
  # print(paste0("delta AICc between m5 and ", aics[1,"rowname"], ": ", aics[1,"AICc"] - m5aic))
  # print(paste0("delta AICc between ,", aics[2,"rowname"], " and ", aics[1,"rowname"], ": ", aics[1,"AICc"] - aics[2,"AICc"]))
  # 
  # str(mod_lists[[winmod]])
  # str(summary(mod_lists[[winmod]]))
  x <- summary(mod_lists[[winmod]])$coefficients %>% data.frame()
  
  out_list[[dim]] <-  summ(mod_lists[[winmod]])
  print(out_list[[dim]])
}



```


Accuracy
```{r Acc model fitting}
m1 <- lmer(TrialSlide_ACC ~ Incongruent + (1|Subject), data = flank_use)
m2 <- lmer(TrialSlide_ACC ~ CongruentBlock + (1|Subject), data = flank_use)
m3 <- lmer(TrialSlide_ACC ~ CongruentBlock*Incongruent + (1|Subject), data = flank_use)
m4 <- lmer(TrialSlide_ACC ~ Incongruent + CongruentBlock + (1|Subject), data = flank_use)
m5 <- lmer(TrialSlide_ACC ~ Incongruent + prev_stim + (1|Subject), data = flank_use)
m6 <- lmer(TrialSlide_ACC ~ Incongruent * prev_stim + (1|Subject), data = flank_use)
m7 <- lmer(TrialSlide_ACC ~ Incongruent + prev_stim + CongruentBlock + (1|Subject), data = flank_use)

MuMIn::AICc(m1,m2,m3, m4,m5, m6,m7)
vif.lme(m5) #looks good, no concerns around collinearity
summ(m4)

m8 <- lmer(TrialSlide_ACC ~ Incongruent + prev_stim + trial_block + (1|Subject), data = flank_use)
m9 <- lmer(TrialSlide_ACC ~ Incongruent + prev_stim + trial_sub + (1|Subject), data = flank_use)
MuMIn::AICc(m5, m8,m9)

```
Accuracy + SNAP dims
```{r}
out_list <- list()
for(dim in names(select(flank_use, contains("Z_")))){
  print(dim)
  #specify candidate models
  f1 <- formula(paste0("TrialSlide_ACC ~ Incongruent + prev_stim + ",dim ," + (1|Subject)"))
  f2 <- formula(paste0("TrialSlide_ACC ~ Incongruent + prev_stim *",dim, "+ (1|Subject)"))
  f2 <- formula(paste0("TrialSlide_ACC ~ Incongruent  *",dim, "+ prev_stim + (1|Subject)"))
  # f4 <- formula(paste0("TrialSlide_ACC ~ CongruentBlock*Incongruent + ",dim, "*CongruentBlock + trial_block + (1|Subject)"))
  
  
  #run candidate models
  mod_lists <- list()
  mod_lists[["m10"]] <- lmer(formula = f1, data = flank_use)
  mod_lists[["m11"]] <- lmer(formula = f2, data = flank_use)
  mod_lists[["m12"]] <- lmer(formula = f3, data = flank_use)
  # mod_lists[["m13"]] <- lmer(formula = f4, data = flank_use)
  
  
  #perform model comparison
  aics <- MuMIn::AICc( mod_lists[["m10"]], mod_lists[["m11"]], mod_lists[["m12"]])%>% rownames_to_column() %>% arrange(AICc)
  aics[,1] <- do.call(rbind,lapply(aics$rowname, function(x)paste0("m",gsub("[^0-9.-]", "", x))))
  
  print(aics)
  
  winmod <- aics[1,"rowname"]
  
  m5aic <- MuMIn::AICc(m5)
  print(paste0("delta AICc between m5 and ", aics[1,"rowname"], ": ", aics[1,"AICc"] - m5aic))
  print(paste0("delta AICc between ,", aics[2,"rowname"], " and ", aics[1,"rowname"], ": ", aics[1,"AICc"] - aics[2,"AICc"]))
  
  out_list[[dim]] <-  summ(mod_lists[[winmod]])
  print(out_list[["m10"]])
  print(out_list[["m11"]])
  print(out_list[["m12"]])
}
```



## HDDM

Once the MLMs and GLMMs are understood, move onto HDDM. :)