---
title: "Flanker Accuracy MLM Trait Relationships for Publication"
subtitle: "PD Inhibition Project"
author: "Michael Hallquist"
date: "29 May 2020"
output:
  html_document:
    code_folding: show
    df_print: default
    mathjax: default
    number_sections: no
    theme: spacelab
    toc: yes
    toc_depth: 2
    toc_float: no
    fig_width: 9
    fig_height: 6
  pdf_document:
    code_folding: hide
    df_print: default
    number_sections: no
    toc: yes
    toc_depth: 4
---
<style type="text/css">
body{ max-width: 2000px; margin: auto; padding: 1em; }
</style>

```{r setup, include=FALSE}
if (!require(pacman)) { install.packages("pacman"); library(pacman) }
p_load(car, nlme, lme4, readr, tidyverse, emmeans, cowplot, MplusAutomation, knitr, sas7bdat, ggcorrplot, psych, lavaan)
knitr::opts_chunk$set(echo = TRUE) #print code by default
#knitr::opts_chunk$set(cache.path = "../../Outputs/flanker_mlms/")
options(digits=3)
options(width=180)

#flanker data processed in flanker_mlm.Rmd
#has the worst subjects removed, rt_inv transformation, etc.
load("../../../Data/preprocessed/flanker_for_traits.RData")
flanker <- flanker %>% mutate(rt_inv=if_else(correct==0, NA_real_, rt_inv),  #treat incorrect RTs as missing
                              prev_rt_z=as.vector(scale(prev_rt)))

#basedir <- "C:/Users/timot/Documents/GitHub/PD_Inhibition_DDM"
basedir <- "~/Data_Analysis/PD_Inhibition_DDM"

mpq <- get(load(file.path(basedir, "Data/preprocessed/MPQ_all_scored_final.RData"))) %>%
  filter(exclude_MPQ == 0) %>% select(subject, MPS_wbR:MPS_abR)
snap <- get(load(file.path(basedir, "Data/preprocessed/SNAP_all_scored_final.RData"))) %>% filter(exclude_SNAP == 0) %>%
  select(subject, NEGTEMP:HDWK, DISINHP)

self_reps <- inner_join(mpq, snap, by = "subject")

mpluscmd <- "/Users/mnh5174/Applications/Mplus/mplus"
#mpluscmd <- "/Applications/Mplus/mplus"
```


# Initial model in Mplus (m15)

This model mimics m15 from flanker ACC mlms for publication. Here, I start out with a two-level model to keep life simpler, rather than having blocks nested within subjects.


```
m15 <- glmer(correct ~ cond + block + prev_rt_z + prev_error +
              (1 + prev_rt_z + cond + prev_error | id) +
              (1 | id:block),
          na.action = na.exclude, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 30000)),
          data = flanker, family=binomial)
```

```{r m15_mplus, cache=TRUE}
m15_mplus <- mplusObject(
  TITLE = "Equivalent model to glmer m15",
  DEFINE = "
    cond = cond - 1; ! 0=congruent, 1=incongruent
    block = block - 1; ! 0=most_incon, 1=most_con
  ",
  VARIABLE = "
    WITHIN = cond block prev_rt_z prev_error;
    USEVARIABLES = id correct cond block prev_rt_z prev_error;
    CLUSTER = id;
    CATEGORICAL = correct;
  ",
  ANALYSIS = "
    TYPE=TWOLEVEL RANDOM;
    ESTIMATOR=BAYES;
    BITERATIONS=(20000) 100000;
    CHAINS=2;
    PROCESSORS=4;
  ",
  MODEL = "
    %WITHIN%
    correct ON block;
    condslo | correct ON cond;        !random slope of cond
    prevslo | correct ON prev_rt_z;   !random slope of rt autocorrelation
    errslo | correct ON prev_error;   !random slope of previous error

    %BETWEEN%
    !means of random slopes
    [condslo];
    [prevslo];
    [errslo];

    !variances of random slopes
    condslo;
    prevslo;
    errslo;

    !slope correlations
    condslo prevslo errslo WITH
       condslo prevslo errslo;

    [correct$1]; !intercept: average correct
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT = "TECH1 TECH8 STANDARDIZED CINTERVAL;",
  rdata = flanker
)

mout <- mplusModeler(m15_mplus, dataout="flanker_acc_mplus.dat",
                     modelout="acc_m15.inp", run=TRUE, hashfilename=FALSE,
                     Mplus_command = mpluscmd)
```

```{r}
summary(mout)
kable(mout$results$parameters$stdyx.standardized %>%
        filter(!paramHeader %in% c("Intercepts", "Means", "Residual Variances")))
```

Looks good compared to the probit version of m15

# ACC: Antagonism + Constraint MSEM

```{r}
tofactor <- self_reps %>% select(subject, MPS_agR, AGG, MISTRUST, MPS_alR, MANIP,
      PROPER, MPS_clR, IMPUL, MPS_tdR, MPS_acR, HDWK) %>%
  mutate(IMPUL =-1*IMPUL) %>% #score toward constraint to make loadings upright
  mutate_at(vars(-subject), list(~as.vector(scale(.)))) %>%
  dplyr::rename(id=subject)

for_msem <- flanker %>% inner_join(tofactor, by="id")
anti_join(tofactor, flanker, by="id")
```

```{r acc_ac, cache=TRUE}
m15_mplus <- mplusObject(
  TITLE="Antagonism and Constraint BSEM CFA 3+3 Parcels, Flanker ACC",
  DEFINE="
    p1=MEAN(MISTRUST MPS_alR);
    p2=MEAN(PROPER MPS_tdR);
    p3=MEAN(MPS_clR IMPUL);
    p4=MEAN(MPS_acR HDWK);
    p5=MEAN(MPS_agR AGG);
    cond = cond - 1; ! 0=congruent, 1=incongruent
    block = block - 1; ! 0=most_incon, 1=most_con
  ",
  VARIABLE = "
    WITHIN = cond block prev_rt_z prev_error;
    USEVARIABLES = id correct cond block prev_rt_z prev_error
          MANIP p1 p2 p3 p4 p5;
    BETWEEN = MANIP p1 p2 p3 p4 p5;
    CLUSTER = id;
    CATEGORICAL = correct;
  ",
  ANALYSIS = "
    TYPE=TWOLEVEL RANDOM;
    ESTIMATOR=BAYES;
    BITERATIONS=(20000) 100000;
    CHAINS=2;
    PROCESSORS=4;
  ",
  MODEL = "
    %WITHIN%
    correct ON block;
    condslo | correct ON cond;        !random slope of cond
    prevslo | correct ON prev_rt_z;   !random slope of rt autocorrelation
    errslo | correct ON prev_error;   !random slope of previous error

    %BETWEEN%
    !means of random slopes
    [condslo];
    [prevslo];
    [errslo];

    !variances of random slopes
    condslo;
    prevslo;
    errslo;

    !slope correlations
    condslo prevslo errslo WITH
       condslo prevslo errslo;

    [correct$1]; !intercept: average correct

    !TRAIT MODEL

    antag BY p5*1 ! MPS_agR AGG
      p1        ! MISTRUST MPS_alR
      MANIP;
    antag@1;

    constraint BY
      p2*  !PROPER MPS_tdR
      p3  !MPS_clR IMPUL
      p4; !MPS_acR HDWK;
    constraint@1;

    antag WITH constraint;

    !TRAIT MODERATION

    ! trait moderates flanker performance -- incongruency effect and stickiness of RT
    condslo ON antag constraint;
    prevslo ON antag constraint;
    errslo ON antag constraint;

    correct ON antag constraint;
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT = "TECH1 TECH8 STANDARDIZED CINTERVAL;",
  rdata = for_msem
)

mout <- mplusModeler(m15_mplus, dataout="flanker_acc_mplus.dat",
                     modelout="acc_m15_AC.inp", run=TRUE, hashfilename = FALSE,
                     Mplus_command = mpluscmd)
```

```{r}
summary(mout)
kable(mout$results$parameters$stdyx.standardized %>%
        filter(!paramHeader %in% c("Intercepts", "Means", "Residual Variances")))

```

# AC MSEM with cross-loading

Between-persons CFA suggests that P1 cross-loads on constraint. Including this cross-loading makes the fit good enough IMO, while without it, CFI is < .9. Do our effects here hold if we allow that?

```{r acc_ac_mod, cache=TRUE}
m15_mplus <- mplusObject(
  TITLE="Antagonism and Constraint BSEM CFA 3+3 Parcels, Flanker ACC Mod",
  DEFINE="
    p1=MEAN(MISTRUST MPS_alR);
    p2=MEAN(PROPER MPS_tdR);
    p3=MEAN(MPS_clR IMPUL);
    p4=MEAN(MPS_acR HDWK);
    p5=MEAN(MPS_agR AGG);
    cond = cond - 1; ! 0=congruent, 1=incongruent
    block = block - 1; ! 0=most_incon, 1=most_con
  ",
  VARIABLE = "
    WITHIN = cond block prev_rt_z prev_error;
    USEVARIABLES = id correct cond block prev_rt_z prev_error
          MANIP p1 p2 p3 p4 p5;
    BETWEEN = MANIP p1 p2 p3 p4 p5;
    CLUSTER = id;
    CATEGORICAL = correct;
  ",
  ANALYSIS = "
    TYPE=TWOLEVEL RANDOM;
    ESTIMATOR=BAYES;
    BITERATIONS=(10000);
    CHAINS=2;
    PROCESSORS=4;
  ",
  MODEL = "
    %WITHIN%
    correct ON block;
    condslo | correct ON cond;        !random slope of cond
    prevslo | correct ON prev_rt_z;   !random slope of rt autocorrelation
    errslo | correct ON prev_error;   !random slope of previous error

    %BETWEEN%
    !means of random slopes
    [condslo];
    [prevslo];
    [errslo];

    !variances of random slopes
    condslo;
    prevslo;
    errslo;

    !slope correlations
    condslo prevslo errslo WITH
       condslo prevslo errslo;

    [correct$1]; !intercept: average correct

    !TRAIT MODEL

    antag BY p5*1 ! MPS_agR AGG
      p1        ! MISTRUST MPS_alR
      MANIP;
    antag@1;

    constraint BY
      p2*  !PROPER MPS_tdR
      p3  !MPS_clR IMPUL
      p4; !MPS_acR HDWK;
    constraint@1;

    antag WITH constraint;

    constraint BY P1; !modification index cross-loading for fit

    !TRAIT MODERATION

    ! trait moderates flanker performance -- incongruency effect and stickiness of RT
    condslo ON antag constraint;
    prevslo ON antag constraint;
    errslo ON antag constraint;

    correct ON antag constraint;
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT = "TECH1 TECH8 STANDARDIZED CINTERVAL;",
  rdata = for_msem
)

mout <- mplusModeler(m15_mplus, dataout="flanker_acc_mplus.dat",
                     modelout="acc_m15_AC_mod.inp", run=TRUE, hashfilename = FALSE,
                     Mplus_command = mpluscmd)
```

```{r}
summary(mout)
kable(mout$results$parameters$stdyx.standardized %>%
        filter(!paramHeader %in% c("Intercepts", "Means", "Residual Variances")))

```


# ACC: Extraversion Model A

Following discussions with the team, Tim examined whether we could get our agency factor to be a bit more pure and less general Extraversion heavy. By dropping POSTEMP and MPS_wbR, we get a very nice agency factor and good fit in CFA.

```{r}
tofactor <- self_reps %>% dplyr::select(subject, POSTEMP, EXHIB, ENTITL, DETACH, MPS_wbR, MPS_spR, MPS_scR) %>%
  mutate(MPS_scR=-1*MPS_scR) %>% #rescore in direction of detachment (higher scores are bad)
  mutate_at(vars(-subject), list(~as.vector(scale(.)))) %>%
  dplyr::rename(id=subject)

for_msem <- flanker %>% inner_join(tofactor, by="id")
anti_join(tofactor, flanker, by="id")
```

```{r E_modela, cache=TRUE}
E_msem <- mplusObject(
  TITLE="Agentic and Affiliative Extraversion MSEM Flanker ACC",
  DEFINE="
    cond = cond - 1; ! 0=congruent, 1=incongruent
    block = block - 1; ! 0=most_incon, 1=most_con
  ",
  VARIABLE = "
    WITHIN = cond block prev_rt_z prev_error;
    USEVARIABLES = id correct cond block prev_rt_z prev_error
      EXHIB ENTITL DETACH MPS_spR MPS_scR;
    BETWEEN = EXHIB ENTITL DETACH MPS_spR MPS_scR;
    CLUSTER = id;
    CATEGORICAL = correct;
  ",
  ANALYSIS = "
    TYPE=TWOLEVEL RANDOM;
    ESTIMATOR=BAYES;
    BITERATIONS=(40000) 100000;
    CHAINS=4;
    PROCESSORS=4;
  ",
  MODEL = "
    %WITHIN%
    correct ON block;
    condslo | correct ON cond;        !random slope of cond
    prevslo | correct ON prev_rt_z;   !random slope of rt autocorrelation
    errslo | correct ON prev_error;   !random slope of previous error

    %BETWEEN%
    !means of random slopes
    [condslo];
    [prevslo];
    [errslo];

    !variances of random slopes
    condslo;
    prevslo;
    errslo;

    !slope correlations
    condslo prevslo errslo WITH
       condslo prevslo errslo;

    [correct$1]; !intercept: average correct

    !TRAIT MODEL
    agentic BY MPS_spR* EXHIB ENTITL;
    agentic@1;

    affiliat BY MPS_scR*1 DETACH;
    affiliat@1;

    agentic WITH affiliat;

    !TRAIT MODERATION

    ! trait moderates flanker performance -- incongruency effect and stickiness of RT
    condslo ON agentic affiliat;
    prevslo ON agentic affiliat;
    errslo ON agentic affiliat;

    !allow proportion correct to be predicted by traits
    correct ON agentic affiliat;
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT ="
    TECH1 TECH8 CINTERVAL STANDARDIZED;
  ",
  rdata=for_msem
)

mres <- mplusModeler(E_msem, modelout = file.path("acc_m15_E.inp"),
                     run=TRUE, hashfilename = FALSE,
                     Mplus_command = mpluscmd)
```
```{r}
summary(mres)
kable(mres$results$parameters$stdyx.standardized %>%
        filter(!paramHeader %in% c("Intercepts", "Means", "Residual Variances")))
```

# ACC: Add agentic Extraversion to Antagonism + Constraint model

```{r}
tofactor <- self_reps %>%
  dplyr::select(subject, EXHIB, ENTITL, DETACH, MPS_spR, MPS_scR,
                MPS_agR, AGG, MISTRUST, MPS_alR, MANIP,
                PROPER, MPS_clR, IMPUL, MPS_tdR, MPS_acR, HDWK) %>%
  mutate(MPS_scR=-1*MPS_scR) %>% #rescore in direction of detachment (higher scores are bad)
  mutate(IMPUL =-1*IMPUL) %>% #score toward constraint to make loadings upright
  mutate_at(vars(-subject), list(~as.vector(scale(.)))) %>%
  dplyr::rename(id=subject)

for_msem <- flanker %>% inner_join(tofactor, by="id")
```

```{r antag_mod_agentic, cache=TRUE}
AC_m15_mplus <- mplusObject(
  TITLE="Antagonism and Constraint BSEM CFA 3+3 Parcels,
    Agentic E, Flanker ACC Mod",
  DEFINE="
    p1=MEAN(MISTRUST MPS_alR);
    p2=MEAN(PROPER MPS_tdR);
    p3=MEAN(MPS_clR IMPUL);
    p4=MEAN(MPS_acR HDWK);
    p5=MEAN(MPS_agR AGG);
    cond = cond - 1; ! 0=congruent, 1=incongruent
    block = block - 1; ! 0=most_incon, 1=most_con
  ",
  VARIABLE = "
    WITHIN = cond block prev_rt_z prev_error;
    USEVARIABLES = id correct cond block prev_rt_z prev_error
      MANIP MPS_spR EXHIB ENTITL 
      p1 p2 p3 p4 p5 ;
    BETWEEN = MANIP MPS_spR EXHIB ENTITL p1 p2 p3 p4 p5;
    CLUSTER = id;
    CATEGORICAL = correct;
  ",
  ANALYSIS = "
    TYPE=TWOLEVEL RANDOM;
    ESTIMATOR=BAYES;
    BITERATIONS=(40000) 100000;
    CHAINS=2;
    PROCESSORS=4;
  ",
  MODEL = "
    %WITHIN%
    correct ON block;
    condslo | correct ON cond;        !random slope of cond
    prevslo | correct ON prev_rt_z;   !random slope of rt autocorrelation
    errslo | correct ON prev_error;   !random slope of previous error

    %BETWEEN%
    !means of random slopes
    [condslo];
    [prevslo];
    [errslo];

    !variances of random slopes
    condslo;
    prevslo;
    errslo;

    !slope correlations
    condslo prevslo errslo WITH
       condslo prevslo errslo;

    [correct$1]; !intercept: average correct

    !TRAIT MODEL

    antag BY p5*1 ! MPS_agR AGG
      p1        ! MISTRUST MPS_alR
      MANIP;
    antag@1;

    constraint BY
      p2*  !PROPER MPS_tdR
      p3  !MPS_clR IMPUL
      p4; !MPS_acR HDWK;
    constraint@1;

    agentic BY MPS_spR* EXHIB ENTITL;
    agentic@1;

    antag WITH constraint;
    antag WITH agentic;
    constraint WITH agentic;

    !two cross-loadings for constraint suggested by MLR
    constraint BY ENTITL;
    constraint BY P1;

    !TRAIT MODERATION

    ! trait moderates flanker performance -- incongruency effect and stickiness of RT
    condslo ON antag constraint agentic;
    prevslo ON antag constraint agentic;
    errslo ON antag constraint agentic;

    correct ON antag constraint agentic;
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT = "TECH1 TECH8 STANDARDIZED CINTERVAL;",
  rdata = for_msem
)

mres <- mplusModeler(AC_m15_mplus, dataout="flanker_acc_mplus.dat",
                     modelout="acc_m15_AC_Eag.inp", run=TRUE, hashfilename = FALSE,
                     Mplus_command = mpluscmd)
```
```{r}
summary(mres)
kable(mres$results$parameters$stdyx.standardized %>%
        filter(!paramHeader %in% c("Intercepts", "Means", "Residual Variances")))
```

# ACC: Add affiliative extraversion to antag + constraint model

```{r acc_ac_mod_affiliat, cache=TRUE}
m15_mplus_affiliat <- mplusObject(
  TITLE="Antagonism and Constraint BSEM CFA 3+3 Parcels,
    Affiliative E, Flanker ACC Mod",
  DEFINE="
    p1=MEAN(MISTRUST MPS_alR);
    p2=MEAN(PROPER MPS_tdR);
    p3=MEAN(MPS_clR IMPUL);
    p4=MEAN(MPS_acR HDWK);
    p5=MEAN(MPS_agR AGG);
    cond = cond - 1; ! 0=congruent, 1=incongruent
    block = block - 1; ! 0=most_incon, 1=most_con
  ",
  VARIABLE = "
    WITHIN = cond block prev_rt_z prev_error;
    USEVARIABLES = id correct cond block prev_rt_z prev_error
      DETACH MPS_scR 
      MANIP p1 p2 p3 p4 p5;
    BETWEEN = DETACH MPS_scR MANIP p1 p2 p3 p4 p5;
    CLUSTER = id;
    CATEGORICAL = correct;
  ",
  ANALYSIS = "
    TYPE=TWOLEVEL RANDOM;
    ESTIMATOR=BAYES;
    BITERATIONS=(40000) 100000;
    CHAINS=2;
    PROCESSORS=4;
  ",
  MODEL = "
    %WITHIN%
    correct ON block;
    condslo | correct ON cond;        !random slope of cond
    prevslo | correct ON prev_rt_z;   !random slope of rt autocorrelation
    errslo | correct ON prev_error;   !random slope of previous error

    %BETWEEN%
    !means of random slopes
    [condslo];
    [prevslo];
    [errslo];

    !variances of random slopes
    condslo;
    prevslo;
    errslo;

    !slope correlations
    condslo prevslo errslo WITH
       condslo prevslo errslo;

    [correct$1]; !intercept: average correct

    !TRAIT MODEL

    antag BY p5*1 ! MPS_agR AGG
      p1        ! MISTRUST MPS_alR
      MANIP;
    antag@1;

    constraint BY
      p2*  !PROPER MPS_tdR
      p3  !MPS_clR IMPUL
      p4; !MPS_acR HDWK;
    constraint@1;

    affiliat BY MPS_scR*1 DETACH;
    affiliat@1;

    antag constraint affiliat WITH antag constraint affiliat;

    !identified in between-persons combined CFA
    AFFILIAT BY P1; !sig modification index

    !TRAIT MODERATION
    condslo ON antag constraint affiliat;
    prevslo ON antag constraint affiliat;
    errslo ON antag constraint affiliat;

    correct ON antag constraint affiliat;
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT = "TECH1 TECH8 STANDARDIZED CINTERVAL;",
  rdata = for_msem
)

mout <- mplusModeler(m15_mplus_affiliat, dataout="flanker_acc_mplus.dat",
                     modelout="acc_m15_AC_Eaf.inp", run=TRUE, hashfilename = FALSE,
                     Mplus_command = mpluscmd)
```

```{r}
summary(mout)
kable(mout$results$parameters$stdyx.standardized %>%
        filter(!paramHeader %in% c("Intercepts", "Means", "Residual Variances")))

```

# ACC: Combined 4-factor model of accuracy

We need two modification indices from the combined CFA to move the model in the right direction.

```{r combined, cache=TRUE}

Combo_msem <- mplusObject(
  TITLE="Combined 4-factor MSEM Flanker ACC",
  DEFINE="
    p1=MEAN(MISTRUST MPS_alR);
    p2=MEAN(PROPER MPS_tdR);
    p3=MEAN(MPS_clR IMPUL);
    p4=MEAN(MPS_acR HDWK);
    p5=MEAN(MPS_agR AGG);
    cond = cond - 1; ! 0=congruent, 1=incongruent
    block = block - 1; ! 0=most_incon, 1=most_con
  ",

  VARIABLE = "
    WITHIN = cond block prev_rt_z prev_error;
    USEVARIABLES = id correct cond block prev_rt_z
      prev_error EXHIB ENTITL DETACH MPS_spR MPS_scR
      MANIP p1 p2 p3 p4 p5;
    BETWEEN = EXHIB ENTITL DETACH MPS_spR MPS_scR MANIP p1 p2 p3 p4 p5;
    CLUSTER = id;
    CATEGORICAL = correct;
  ",
  ANALYSIS = "
    TYPE=TWOLEVEL RANDOM;
    ESTIMATOR=BAYES;
    BITERATIONS=(40000) 100000;
    CHAINS=4;
    PROCESSORS=4;
  ",
  MODEL = "

%WITHIN%
    correct ON block;
    condslo | correct ON cond;        !random slope of cond
    prevslo | correct ON prev_rt_z;   !random slope of rt autocorrelation
    errslo | correct ON prev_error;   !random slope of previous error

    %BETWEEN%
    !means of random slopes
    [condslo];
    [prevslo];
    [errslo];

    !variances of random slopes
    condslo;
    prevslo;
    errslo;

    !slope correlations
    condslo prevslo errslo WITH
       condslo prevslo errslo;

    [correct$1]; !intercept: average correct

    !TRAIT MODEL
    agentic BY MPS_spR* EXHIB ENTITL;
    agentic@1;

    affiliat BY MPS_scR*1 DETACH;
    affiliat@1;

    antag BY p5* ! MPS_agR AGG
      p1        ! MISTRUST MPS_alR
      MANIP;
    antag@1;

    constraint BY
      p2*  !PROPER MPS_tdR
      p3  !MPS_clR IMPUL
      p4; !MPS_acR HDWK;
    constraint@1;

    antag constraint agentic affiliat WITH 
      antag constraint agentic affiliat;

    !identified in between-persons combined CFA
    AFFILIAT BY P1; !sig modification index
    constraint BY ENTITL; !sig modification index

    !TRAIT MODERATION

    condslo ON antag constraint agentic affiliat;
    prevslo ON antag constraint agentic affiliat;
    errslo ON antag constraint agentic affiliat;

    !allow proportion correct to be predicted by traits
    correct ON antag constraint agentic affiliat;
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT ="
    TECH1 TECH8 CINTERVAL STANDARDIZED;
  ",
  rdata=for_msem
)

mres <- mplusModeler(Combo_msem, modelout = file.path("acc_m15_ACE.inp"),
                     run=TRUE, hashfilename = FALSE, 
                     Mplus_command = mpluscmd)
```
```{r}
summary(mres)
kable(mres$results$parameters$stdyx.standardized %>%
        filter(!paramHeader %in% c("Intercepts", "Means", "Residual Variances")))
```
