---
title: "Flanker MLM Trait Relationships"
subtitle: "PD Inhibition Project"
author: "Michael Hallquist"
date: "5 Apr 2020"
output:
  html_document:
    code_folding: show
    df_print: default
    mathjax: default
    number_sections: no
    theme: spacelab
    toc: yes
    toc_depth: 2
    toc_float: yes
    fig_width: 9 
    fig_height: 6 
  pdf_document:
    code_folding: hide
    df_print: default
    number_sections: no
    toc: yes
    toc_depth: 4
---
<style type="text/css">
body{ max-width: 2000px; margin: auto; padding: 1em; }
</style>

```{r setup, include=FALSE}
if (!require(pacman)) { install.packages("pacman"); library(pacman) }
p_load(car, nlme, lme4, readr, tidyverse, emmeans, cowplot, MplusAutomation, knitr, sas7bdat, ggcorrplot, psych, lavaan)
knitr::opts_chunk$set(echo = TRUE) #print code by default
#knitr::opts_chunk$set(cache.path = "../../Outputs/flanker_mlms/")
options(digits=3)
options(width=180)
```

# Data cleaning and setup

```{r}
#flanker data processed in flanker_mlm.Rmd
#has the worst subjects removed, rt_inv transformation, etc.
load("../../Data/preprocessed/flanker_for_traits.RData")
```

## prepare for mplus
```{r}
prepareMplusData(flanker, filename="flanker_mplus.dat")
```

# Initial model in Mplus

This model mimics m30 from flanker_mlms, though I did not try to accommodate heterogeneous variance at L1 (which is a pain).

I also haven't validated it closely and should probably spend a little more time looking at the details.

```
m30 <-  lme(rt_inv ~ run_trial_z + trial_z + cond*block + prev_rt, 
          random=list(id=~ 1 + run_trial_z + trial_z + cond + prev_rt, block=~1 + run_trial_z + trial_z),
          weights=varIdent(form=~1|block*cond),
          na.action = na.exclude,
          data = flanker, method='ML', control = lmeControl(opt="optim")) #lmeControl(maxIter = 200, msMaxIter = 200))
```


```{r m30_mplus, cache=TRUE}
m30_mplus <- mplusObject(
  TITLE = "Equivalent model to lme m30",
  DEFINE = "
    cond = cond - 1; ! 0=congruent, 1=incongruent
    block = block - 1; ! 0=most_incon, 1=most_con
    cond_block = cond*block; ! 1=most_con, incongruent
  ",
  VARIABLE = "
    WITHIN = cond block cond_block prev_rt trial_z run_trial_z;
    USEVARIABLES = id rt_inv cond block prev_rt trial_z run_trial_z cond_block;
    CLUSTER = id;
  ",
  ANALYSIS = "
    TYPE=TWOLEVEL RANDOM;
    ESTIMATOR=BAYES;
    FBITERATIONS=10000;
    CHAINS=2;
    PROCESSORS=4;
  ",
  MODEL = "
    %WITHIN%
    rt_inv ON block cond_block;
    condslo | rt_inv ON cond;
    runslo | rt_inv ON run_trial_z;
    trialslo | rt_inv ON trial_z;
    prevslo | rt_inv ON prev_rt;
    
    %BETWEEN%
    !means of random slopes
    [condslo];
    [runslo];
    [trialslo];
    [prevslo];
    
    !variances of random slopes
    condslo;
    runslo;
    trialslo;
    prevslo;
    
    !slope correlations
    condslo runslo trialslo prevslo WITH
       condslo runslo trialslo prevslo;
    
    [rt_inv]; !mean average inverse RT
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT = "TECH1 TECH8 STANDARDIZED CINTERVAL;",
  rdata = flanker
)

mout <- mplusModeler(m30_mplus, dataout="flanker_mplus.dat", 
                        modelout="m30_mplus.inp", run=TRUE)

results <- mout$results

```

Should run_trial_z and trial_z be WITHIN variables? Doesn't seem like we care about the between component of these. For now, I have put them as WITHIN. 
But could revisit if there is any reason to anticipate a meaningful between-subjects latent variables for these.

## Unstandardized effects

```{r}
kable(results$parameters$unstandardized)
```

## Standardized effects

```{r}
kable(results$parameters$stdyx)
```

## Summary

Although it's a little more legwork to look for the right parameters since some show up as means (random slopes) and others as fixed effect parameters, there is a high degree of convergence between this output and m30.

# Trait overview

Just prototyping here... Get SNAP scores and try to build an antagonism factor.

```{r}
snap_scores <- read.sas7bdat("~/TresorSync/Grad_School/Dissertation/Analyses/Data/snap2scores.sas7bdat") %>%
  select(subject, starts_with("T_")) %>% dplyr::rename(id=subject)
```

## Quick EFA

Drop validity scales for a minute, as well as higher-order scales, look at spectrum

```{r}
to_efa <- snap_scores %>% select(-id, -T_InvalidityIndex, -T_RareVirtues, -T_Deviance, -T_BackDeviance, -T_TRIN, -T_VRIN, -T_DRIN,
                                 -T_NegativeTemperament, -T_PositiveTemperament, -T_Disinhibition, #higher-order scales
                                 -T_SuicideProneness, -T_LowSelfEsteem) #these have item overlap with self-harm
eigen(cor(to_efa))$values
```

### Correlation plot of 12 SNAP scales
```{r, fig=TRUE, width=10, height=10}
ggcorrplot(to_efa %>% cor(), hc.order = TRUE)
```


### 4-factor EFA (Kaiser's rule)

```{r}
fa4 <- fa(to_efa, nfactors = 4, fm="ml")
fa4
```

### 3-factor EFA

Self-harm likes to stay to itself. Reduce to 3-factor solution
```{r}
fa3 <- fa(to_efa, nfactors = 3, fm="ml")
fa3
```

### Simple antagonism factor

Try 1-factor model with Mistrust, Manipulativeness, Aggression, and Self-Harm

Detachment is squirrelly

```{r}
pathology1 <- "
 f =~ T_Mistrust + T_Manipulativeness + T_Aggression + T_SelfHarm # + T_Detachment
"

m1 <- cfa(pathology1, data=snap_scores, estimator="MLR")
summary(m1, fit.measures=TRUE, standardized=TRUE)
modificationindices(m1, minimum.value = 4)
```

# Trait - flanker MSEM prototype

Add relevant SNAP scores to Mplus dataset, then fit MSEM model with traits as moderator of congruency random slope

```{r}
flanker_traits <- full_join(snap_scores %>% select(id, T_Mistrust, T_Manipulativeness, T_Aggression, T_SelfHarm),
                            flanker, by="id")
```

## Corroborate 1-factor model in simple between-subjects Mplus

```{r mplus_1fac, cache=TRUE}
mplus_trait <- mplusObject(
  TITLE = "Antagonismesque factor",
  VARIABLE = "
    USEVARIABLES = T_Mistrust T_Manipulativeness T_Aggression T_SelfHarm;
  ",
  ANALYSIS = "
    ESTIMATOR=BAYES;
    FBITERATIONS=10000;
    CHAINS=2;
    PROCESSORS=4;
  ",
  MODEL = "
    ! trait model
    antag BY T_Mistrust T_Manipulativeness T_Aggression T_SelfHarm;
    
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT = "TECH1 TECH8 STANDARDIZED CINTERVAL;",
  rdata = snap_scores %>% select(id, T_Mistrust, T_Manipulativeness, T_Aggression, T_SelfHarm)
)

mout_trait <- mplusModeler(mplus_trait, dataout="traits_mplus.dat", 
                        modelout="mplus_antag.inp", run=TRUE)

trait_antag <- mout_trait$results
```

### Unstandardized effects

```{r}
kable(trait_antag$parameters$unstandardized)
```

### Standardized effects

```{r}
kable(trait_antag$parameters$stdyx)
```

Looks very clean -- not perfect (RMSEA) -- and comparable to lavaan

## Full MSEM with Antagonism as predictor (moderator) of random slopes

```{r m30_trait, cache=TRUE}
m30_mplus_trait <- mplusObject(
  TITLE = "Antagonismesque factor and flanker",
  DEFINE = "
    cond = cond - 1; ! 0=congruent, 1=incongruent
    block = block - 1; ! 0=most_incon, 1=most_con
    cond_block = cond*block; ! 1=most_con, incongruent
  ",
  VARIABLE = "
    WITHIN = cond block cond_block prev_rt trial_z run_trial_z;
    BETWEEN = T_Mistrust T_Manipulativeness T_Aggression T_SelfHarm;
    USEVARIABLES = id rt_inv cond block prev_rt trial_z run_trial_z 
      T_Mistrust T_Manipulativeness T_Aggression T_SelfHarm cond_block;
    CLUSTER = id;
  ",
  ANALYSIS = "
    TYPE=TWOLEVEL RANDOM;
    ESTIMATOR=BAYES;
    FBITERATIONS=10000;
    CHAINS=2;
    PROCESSORS=4;
  ",
  MODEL = "
    %WITHIN%
    rt_inv ON block cond_block;
    condslo | rt_inv ON cond;
    runslo | rt_inv ON run_trial_z;
    trialslo | rt_inv ON trial_z;
    prevslo | rt_inv ON prev_rt;
    
    %BETWEEN%
    
    !means of random slopes
    [condslo];
    [runslo];
    [trialslo];
    [prevslo];
    
    !variances of random slopes
    condslo;
    runslo;
    trialslo;
    prevslo;
    
    !slope correlations (removed because all n.s.)
    !condslo runslo trialslo prevslo WITH
    !   condslo runslo trialslo prevslo;
    
    [rt_inv]; !mean average inverse RT
    
    ! trait model
    antag BY T_Mistrust T_Manipulativeness T_Aggression T_SelfHarm;

    ! trait moderates flanker performance -- incongruency effect and stickiness of RT
    condslo ON antag;
    prevslo ON antag;
    
    !N.B. Leaving out the association of antag with rt_inv omits a hugely important relationship
    !  on the between level and will lead to bizarre problems -- like factor loadings near zero
    
    !allow antag as a predictor of average RT
    rt_inv ON antag;
    
    ! let factor correlate with other variables on the between level
    ! omitting this for now because it leads to estimation problems at times and when added individually, these are highly n.s.
    !antag WITH runslo;
    !antag WITH trialslo;
    
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT = "TECH1 TECH8 STANDARDIZED CINTERVAL;",
  rdata = flanker_traits
)

mout_antag <- mplusModeler(m30_mplus_trait, dataout="flanker_traits_mplus.dat", 
                        modelout="m30_mplus_antag.inp", run=TRUE)

results_antag <- mout_antag$results

```

### Unstandardized effects

```{r}
kable(results_antag$parameters$unstandardized)
```

### Standardized effects

```{r}
kable(results_antag$parameters$stdyx)
```

### Conclusions:

1. Sweet, we see that the factor moderates key performance measures!!
2. First, we see that greater antagonism is associated with longer RTs on incongruent relative to congruent trials, $\beta = .37, p = .01$ (CONDSLO.ON ANTAG)
3. Higher antagonism is associated with faster RTs overall (tendency to respond quickly): $\beta = -.51, p = .001$ (RT_INV.ON ANTAG)
4. Higher antagonism is associated with stronger RT stickiness (AR1 effect): $\beta = .52, p = .009$ (prevslo.ON ANTAG)

# Antagonism (ish) MSEM that includes accuracy as well

One beautiful thing about the MSEM approach here is that we can scale to a simultaneous analysis of accuracy by having a multivariate model at the within level. Let's try it!

This model, though, is slightly tortured by the number of random slopes and possibilities for modeling at the between-person level. Although there is a strong relationship of `prev_rt`
with `b_prevslo` (the within-trial association of accuracy with prior RT), it gets tricky to relate this to the factor. Basically, adding a `b_prevslo ON antag` statement drives the model off
the rails in all the variants I have tested. Here's a model that keeps things on the rails... Below is a model for accuracy alone (not accuracy + RT).

```{r m30_trait_correct, cache=TRUE}
m30_mplus_trait_correct <- mplusObject(
  TITLE = "Antagonismesque factor and flanker",
  DEFINE = "
    cond = cond - 1; ! 0=congruent, 1=incongruent
    block = block - 1; ! 0=most_incon, 1=most_con
    cond_block = cond*block; ! 1=most_con, incongruent
  ",
  VARIABLE = "
    WITHIN = cond block cond_block prev_rt trial_z run_trial_z;
    BETWEEN = T_Mistrust T_Manipulativeness T_Aggression T_SelfHarm;
    USEVARIABLES = id correct rt_inv cond block prev_rt trial_z run_trial_z 
      T_Mistrust T_Manipulativeness T_Aggression T_SelfHarm cond_block;
    CLUSTER = id;
    CATEGORICAL = correct;
  ",
  ANALYSIS = "
    TYPE=TWOLEVEL RANDOM;
    ESTIMATOR=BAYES;
    BITERATIONS=(15000);
    BCONVERGENCE=.02;
    CHAINS=2;
    PROCESSORS=4;
  ",
  MODEL = "
    %WITHIN%
    rt_inv ON block cond_block;
    condslo | rt_inv ON cond;
    runslo | rt_inv ON run_trial_z;
    trialslo | rt_inv ON trial_z;
    prevslo | rt_inv ON prev_rt;
    
    !treat these as fixed only (keep the model sane)
    correct ON trial_z run_trial_z block cond_block;
    b_condslo | correct ON cond;
    b_prevslo | correct ON prev_rt;
    
    correct WITH rt_inv; !allow RT-accuracy correlation
    
    %BETWEEN%
    
    !means of random slopes
    [condslo];
    [runslo];
    [trialslo];
    [prevslo];
    
    !variances of random slopes
    condslo;
    runslo;
    trialslo;
    prevslo;
    
    !slope correlations (removed because all n.s.)
    !condslo runslo trialslo prevslo WITH
    !   condslo runslo trialslo prevslo;
    
    [rt_inv]; !mean average inverse RT
    
    ! trait model
    antag BY T_Mistrust T_Manipulativeness T_Aggression T_SelfHarm;

    ! trait moderates flanker performance -- incongruency effect and stickiness of RT
    condslo ON antag;
    prevslo ON antag;
    
    !N.B. Leaving out the association of antag with rt_inv omits a hugely important relationship
    !  on the between level and will lead to bizarre problems -- like factor loadings near zero
    
    !allow antag as a predictor of average RT
    rt_inv ON antag;
    
    ! let factor correlate with other variables on the between level
    ! omitting this for now because it leads to estimation problems at times and when added individually, these are highly n.s.
    !antag WITH runslo;
    !antag WITH trialslo;
    
    [correct$1]; !person average
    b_condslo ON antag; !whether antagonism moderates the incongruency -> accuracy relationship
    
    b_prevslo WITH antag; !drives the model off the rails if we attempt b_prevslo ON antag
    
    !allow antag as predictor of overall accuracy
    correct on antag;
    
    !relationship between average RT and accuracy
    correct WITH rt_inv;
    
    !associations between continuous and binary random slopes
    !condslo WITH b_condslo;
    !prevslo WITH b_prevslo;
    
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT = "TECH1 TECH8 STANDARDIZED CINTERVAL;",
  rdata = flanker_traits
)

mout_antag_correct <- mplusModeler(m30_mplus_trait_correct, dataout="flanker_traits_mplus.dat", 
                        modelout="m30_mplus_antag_correct.inp", run=TRUE)

results_antag_correct <- mout_antag_correct$results

```

## Unstandardized effects

```{r}
kable(results_antag_correct$parameters$unstandardized)
```

## Standardized effects

```{r}
kable(results_antag_correct$parameters$stdyx)
```

# Simpler MSEM for accuracy alone

```{r m30_trait_accalone, cache=TRUE}
m30_mplus_trait_accalone <- mplusObject(
  TITLE = "Antagonismesque factor and flanker",
  DEFINE = "
    cond = cond - 1; ! 0=congruent, 1=incongruent
    block = block - 1; ! 0=most_incon, 1=most_con
    cond_block = cond*block; ! 1=most_con, incongruent
  ",
  VARIABLE = "
    WITHIN = cond block cond_block prev_rt trial_z run_trial_z;
    BETWEEN = T_Mistrust T_Manipulativeness T_Aggression T_SelfHarm;
    USEVARIABLES = id correct cond block prev_rt trial_z run_trial_z 
      T_Mistrust T_Manipulativeness T_Aggression T_SelfHarm cond_block;
    CLUSTER = id;
    CATEGORICAL = correct;
  ",
  ANALYSIS = "
    TYPE=TWOLEVEL RANDOM;
    ESTIMATOR=BAYES;
    BITERATIONS=(15000);
    BCONVERGENCE=.02;
    CHAINS=2;
    PROCESSORS=4;
  ",
  MODEL = "
    %WITHIN%
    !treat these as fixed only (keep the model sane)
    correct ON trial_z run_trial_z block cond_block;
    b_condslo | correct ON cond;
    b_prevslo | correct ON prev_rt;
    
    %BETWEEN%
    [b_condslo b_prevslo]; !slope means
    b_condslo b_prevslo; !slope variances
    
    ! trait model
    antag BY T_Mistrust T_Manipulativeness T_Aggression T_SelfHarm;

    [correct$1]; !person average
    b_condslo ON antag; !whether antagonism moderates the incongruency -> accuracy relationship
    b_prevslo ON antag; !whether antagonism moderates the prev_rt -> accuracy relationship
    
    !allow antag as predictor of overall accuracy
    correct on antag;
    
    !correlation of random slopes with each other
    b_condslo WITH b_prevslo;
  ",
  PLOT = "TYPE = PLOT2;",
  OUTPUT = "TECH1 TECH8 STANDARDIZED CINTERVAL;",
  rdata = flanker_traits
)

mout_antag_accalone <- mplusModeler(m30_mplus_trait_accalone, dataout="flanker_traits_mplus.dat", 
                        modelout="m30_mplus_antag_accalone.inp", run=TRUE)

results_antag_accalone <- mout_antag_accalone$results

```

## Unstandardized effects

```{r}
kable(results_antag_accalone$parameters$unstandardized)
```

## Standardized effects

```{r}
kable(results_antag_accalone$parameters$stdyx)
```

Overall, the main finding here is that more antagonistic folks are more inaccurate on average. There is a trend toward the prev_rt -> accuracy effect being moderated by antagonism. It's reassuring that the key effects here replicate the RT + accuracy model above, even with the dreaded b_prevslo ON antag` effect in the model.