---
title: "Final Flanker Accuracy Analyses"
subtitle: "PD Inhibition Project"
author: "Michael Hallquist"
date: "28 May 2020"
output: 
  html_document:
    code_folding: show
    df_print: default
    mathjax: default
    number_sections: no
    theme: spacelab
    toc: yes
    toc_depth: 2
    toc_float: no
    fig_width: 9 
    fig_height: 6 
  pdf_document:
    df_print: default
    number_sections: no
    toc: yes
    toc_depth: 4
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require(pacman)) { install.packages("pacman"); library(pacman) }
p_load(car, nlme, lme4, readr, tidyverse, emmeans, cowplot, bbmle, broom, knitr, kableExtra, flextable, stargazer, lmerTest)
knitr::opts_chunk$set(echo = TRUE) #print code by default
#knitr::opts_chunk$set(cache.path = "../../Outputs/flanker_mlms/")
#options(digits=2)
options(scipen = 2, digits = 3)
options(width = 140)
emm_options(disable.pbkrtest = TRUE, lmerTest.limit=2e4) #disable KR and estimate Satterthwaite

#preprocessed in flanker_mlm.Rmd
load(file="../../Data/preprocessed/flanker_for_traits.RData")
flanker <- flanker %>% filter(exclude < 3) %>% #least restrictive exclusions
  mutate(prev_rt=prev_rt - mean(prev_rt, na.rm=TRUE),
         prev_rt_z = as.vector(scale(prev_rt))) #z-score rt to put parameter estimates on smaller scale

render_aictab <- function(minfo, ...) {
  mc <- match.call(expand.dots = TRUE)
  mlist <- list(...)
  
  #N.B. AICtab fails if you try to assign names to the list names(mlist) <- ...
  mnames <- sapply(3:length(mc), function(x) { as.character(mc[[x]])})
  mdf <- do.call(rbind, minfo) %>% as.data.frame() %>% rownames_to_column("model")
  adf <- AICtab(mlist, sort=FALSE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE, mnames=mnames) %>% 
    as.data.frame() %>% rownames_to_column("model") %>% dplyr::select(-dLogLik)

  res <- mdf %>% left_join(adf, by="model")
  return(res)
}

flextb_vif <- function(m) {
  flextable(data.frame(vif=car::vif(m)) %>% rownames_to_column("Predictor")) %>% autofit()
}

check_singularity <- function(lmerobj) {
  tt <- getME(lmerobj,"theta") #RE estimates
  ll <- getME(lmerobj,"lower") #lower bound on estimate
  
  #look for RE estimates that are very small (near zero) and the lower bound encompasses 0
  low_re <- tt[ll==0 & tt < 1e-2]
  return(low_re)
  
  #eventually, would be nice to provide functionality to drop these from model and refit automatically
}

minfo <- list() #used for building model summary table
```

This file contains final MLMs for accuracy statistics on the flanker task for the PD Inhibition DDM project.

## m0: design effects, no interaction, random intercept of subject

```{r}
minfo <- list() #re-initialize now that we're eliminating l1 heterogeneity
minfo[["m0"]] <- c(fixed="Congruency, Block", l2="Subject: Intercept")
```

```{r m0_lmer, cache=TRUE}
m0 <- glmer(correct ~ cond + block + (1|id),
          na.action = na.exclude, 
          data = flanker, family=binomial)
```

```{r}
flextable(car::Anova(m0, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
flextb_vif(m0)
emmeans(m0, ~cond|block, type="response")
anova(m0)
```

## m1: design effects, random intercept of subject

Allow for interaction of congruency and block

```{r}
minfo[["m1"]] <- c(fixed="Congruency, Block, Congruency x Block", l2="Subject: Intercept")
```

```{r m1_lmer, cache=TRUE}
m1 <- glmer(correct ~ cond*block + (1|id),
          na.action = na.exclude, 
          data = flanker, family=binomial)
```

```{r}
#flextable(anova(m1) %>% rownames_to_column("Effect")) %>% autofit() #lmerTest reports Satterthwaite degrees of freedom
flextable(car::Anova(m1, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
flextb_vif(m1)
anova(m1)

flextable(as.data.frame(emmeans(m1, ~cond|block, type="response")) %>% dplyr::select(-df)) %>% 
  colformat_num(j=c("prob", "SE", "asymp.LCL", "asymp.UCL"), digits=3)  %>% autofit()
flextable(render_aictab(minfo=minfo, m0, m1)) %>% autofit()
```

Conclusion: no significant condition x block interaction. Drop from subsequent models for simplicity. Also, the interaction is collinear with the condition.

## m2: design effects, allow for L2 random intercept to vary by block

Use nested RE specification.

```{r}
minfo[["m2"]] <- c(
  fixed="Congruency, Block",
  l2="Subject: Intercept\nBlock within subject: Intercept")
```

```{r m2_lmer, cache=TRUE}
m2 <- glmer(correct ~ cond + block + (1|id/block),
          na.action = na.exclude,
          data = flanker, family=binomial, nAGQ=1)
```

```{r}
car::Anova(m2, type=3)
anova(m2)
flextable(render_aictab(minfo=minfo, m0, m1, m2)) %>% autofit()
```

## m3: Add trial_z as fixed

Non-significant effect -- do not pursue

```{r}
minfo[["m3"]] <- c(
  fixed="Congruency, Block, Trial", 
  l2="Subject: Intercept\nBlock within subject: Intercept")
```

```{r m3_lmer, cache=TRUE}
m3 <- glmer(correct ~ cond + block + trial_z + (1|id/block),
          na.action = na.exclude,
          data = flanker, family=binomial)
```

```{r}
flextable(car::Anova(m3, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
flextable(render_aictab(minfo=minfo, m0, m1, m2, m3)) %>% autofit()
```

## m4: Add trial_z as random only at subject level, not block-specific

And drop fixed effect of trial_z from m3

```{r}
minfo[["m4"]] <- c(
  fixed="Congruency, Block", 
  l2="Subject:Intercept, Trial\nBlock within subject: Intercept")
```

```{r m4_lmer, cache=TRUE, include=FALSE}
m4 <- glmer(correct ~ cond + block + (1 + trial_z | id) + (1 | id:block),
          na.action = na.exclude,
          data = flanker, family=binomial)
```

```{r}
flextable(car::Anova(m4, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
flextable(render_aictab(minfo=minfo, m0, m1, m2, m3, m4)) %>% autofit()
```

## m5: Add trial_z as random both per subject and block

And drop trial_z as fixed

```{r}
minfo[["m5"]] <- c(
  fixed="Congruency, Block",
  l2="Subject: Intercept, Trial\nBlock within subject: Intercept, Trial")
```

```{r m5_lmer, cache=TRUE}
m5 <- glmer(correct ~ cond + block + (1 + trial_z | id/block),
          na.action = na.exclude,
          data = flanker, family=binomial)
```

```{r}
summary(m5)
flextb_vif(m5)
flextable(car::Anova(m5, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
flextable(render_aictab(minfo=minfo, m0, m1, m2, m3, m4, m5)) %>% autofit()
```

In short, no evidence that trial helps our accuracy models at all.

## m6: Add trial x block interaction as fixed, remove trial_z random

```{r}
minfo[["m6"]] <- c(
  fixed="Congruency, Block, Trial, Block x Trial", 
  l2="Subject: Intercept\nBlock within subject: Intercept")
```

```{r m6_lmer, cache=TRUE}
m6 <- glmer(correct ~ cond + block + trial_z*block + (1 | id/block),
          na.action = na.exclude,
          data = flanker, family=binomial)
```

```{r}
flextb_vif(m6)
flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5, m6)) %>% autofit()
```

No support for trial x block (and collinearity concern)

## m7: Trial within run (run_trial) as fixed

Marginal fixed effect. Keep it to be on the liberal end

```{r}
minfo[["m7"]] <- c(
  fixed="Congruency, Block, Run Trial", 
  l2="Subject: Intercept, Trial\nBlock within subject: Intercept, Trial")
```

```{r m7_lmer, cache=TRUE}
m7 <- glmer(correct ~ cond + block + run_trial_z + (1 | id/block),
          na.action = na.exclude,
          data = flanker, family=binomial)
```

```{r}
flextable(car::Anova(m7, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
flextable(render_aictab(minfo=minfo, m0, m1, m2, m3, m4, m5, m6, m7)) %>% autofit()
```

## m8: Trial within run as random

Not an improvement, don't consider the id versus id/block split for run_trial_z

```{r}
minfo[["m8"]] <- c(
  fixed="Congruency, Block", 
  l2="Subject: Intercept, Run Trial\nBlock within subject: Intercept, Run Trial")
```

```{r m8_lmer, cache=TRUE}
m8 <- glmer(correct ~ cond + block + run_trial_z + (1 + run_trial_z | id/block),
          na.action = na.exclude,
          data = flanker, family=binomial)
```

```{r}
flextable(render_aictab(minfo=minfo, m0, m1, m2, m3, m4, m5, m6, m7, m8)) %>% autofit()
```

## m9: Add prev_rt_z as fixed effect

Has a substantial effect!

```{r}
minfo[["m9"]] <- c(
  fixed="Congruency, Block, Previous RT, Run Trial", 
  l2="Subject: Intercept, Block within subject: Intercept")
```

```{r m9_lmer, cache=TRUE}
m9 <- glmer(correct ~ cond + block + prev_rt_z + run_trial_z + (1 | id/block),
          na.action = na.exclude,
          data = flanker, family=binomial)
```

```{r}
flextb_vif(m9)

flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5, m6, m7, m8, m9)) %>% autofit()
```

## m10: Add prev_rt_z as random at subject level only

```{r}
minfo[["m10"]] <- c(
  fixed="Congruency, Block, Previous RT, Run Trial", 
  l2="Subject: Intercept, Previous RT,\nBlock within subject: Intercept")
```

```{r m10_lmer, cache=TRUE}
m10 <- glmer(correct ~ cond + block + prev_rt_z + run_trial_z + (1 + prev_rt_z | id) + (1 | id:block),
          na.action = na.exclude, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 30000)),
          data = flanker, family=binomial)
```

```{r}
flextb_vif(m10)

flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5, m6, m7, m8, m9, m10)) %>% autofit()
```

## m11: Add prev_rt_z as random at subject and block level

This yields a singular fit that is attributable to the variance of prev_rt_z at block within id level. Thus, although it technically improves fit a tiny bit (AIC diff ~0.5), don't retain it.

```{r}
minfo[["m11"]] <- c(
  fixed="Congruency, Block, Previous RT, Run Trial", 
  re_details="Subject:Intercept, Previous RT,\nBlock within subject: Intercept, Previous RT")
```

```{r m11_lmer, cache=TRUE}
m11 <- glmer(correct ~ cond + block + prev_rt_z + run_trial_z + (1 + prev_rt_z | id/block),
          na.action = na.exclude, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 30000)),
          data = flanker, family=binomial)
```

```{r}
if (isSingular(m11)) { check_singularity(m11) }
flextb_vif(m11)

flextable(car::Anova(m11, type=3) %>% rownames_to_column("Predictor")) %>% autofit()

flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11)) %>% autofit()
```

## m12: Add condition as random at subject level

Run trial makes this model go off the rails (poor convergence). Drop (in m13)

```{r}
minfo[["m12"]] <- c(
  fixed="Congruency, Block, Previous RT, Run Trial", 
  l2="Subject: Intercept, Previous RT, Congruency\nBlock within subject: Intercept")
```

```{r m12_lmer, cache=TRUE}
m12 <- glmer(correct ~ cond + block + prev_rt_z + run_trial_z +
              (1 + prev_rt_z + cond | id) +
              (1 | id:block),
          na.action = na.exclude, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 30000)),
          data = flanker, family=binomial)
```

```{r}
if (isSingular(m12)) { check_singularity(m12) }
flextb_vif(m12)

flextable(car::Anova(m12, type=3) %>% rownames_to_column("Predictor")) %>% autofit()

flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12)) %>% autofit()

```

## m13: drop run_trial_z as fixed

We only see a small decrement in fit. AIC goes up ~.15, so let's go with the more parsimonious model that converges!

```{r}
minfo[["m13"]] <- c(
  fixed="Congruency, Block, Previous RT", 
  l2="Subject: Intercept, Previous RT, Congruency\nBlock within subject: Intercept")
```

```{r m13_lmer, cache=TRUE}
m13 <- glmer(correct ~ cond + block + prev_rt_z +
              (1 + prev_rt_z + cond | id) +
              (1 | id:block),
          na.action = na.exclude, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 30000)),
          data = flanker, family=binomial)
```

```{r}
if (isSingular(m13)) { check_singularity(m13) }
flextb_vif(m13)

flextable(car::Anova(m13, type=3) %>% rownames_to_column("Predictor")) %>% autofit()

flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12, m13)) %>% autofit()

```

## m14: add prev_error as fixed

Post-error shifts toward accuracy? No, p = .51, nothing to it

```{r}
minfo[["m14"]] <- c(
  fixed="Congruency, Block, Previous RT, Previous Error", 
  l2="Subject: Intercept, Previous RT, Congruency\nBlock within subject: Intercept")
```

```{r m14_lmer, cache=TRUE}
m14 <- glmer(correct ~ cond + block + prev_rt_z + prev_error +
              (1 + prev_rt_z + cond | id) +
              (1 | id:block),
          na.action = na.exclude, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 30000)),
          data = flanker, family=binomial)
```

```{r}
flextb_vif(m14)

flextable(car::Anova(m14, type=3) %>% rownames_to_column("Predictor")) %>% autofit()

flextable(render_aictab(minfo=minfo, m0, m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12, m13, m14)) %>% autofit()
```

## m15: allow prev_error to be random at subject level

Keep the fixef for now to ensure it stays at zero with random in the model. Looks like there is meaningful heterogeneity in whether a previous error influence accuracy on this trial. Actually, when we include the RE, the FE becomes sig.

```{r}
minfo[["m15"]] <- c(
  fixed="Congruency, Block, Previous RT, Previous Error", 
  l2="Subject: Intercept, Previous RT, Congruency, Previous Error\nBlock within subject: Intercept")
```

```{r m15_lmer, cache=TRUE}
m15 <- glmer(correct ~ cond + block + prev_rt_z + prev_error +
              (1 + prev_rt_z + cond + prev_error | id) +
              (1 | id:block),
          na.action = na.exclude, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 30000)),
          data = flanker, family=binomial)
```


```{r}
if (isSingular(m15)) { check_singularity(m15) }
flextb_vif(m15)
flextable(car::Anova(m15, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
flextable(render_aictab(minfo=minfo, m0, m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12, m13, m14, m15)) %>% autofit()
```

## m16: add interaction back in for reporting purposes

```{r}
minfo[["m16"]] <- c(
  fixed="Congruency, Block, Congruency x Block, Previous RT, Previous Error", 
  l2="Subject: Intercept, Previous RT, Congruency, Previous Error\nBlock within subject: Intercept")
```

```{r m16_lmer, cache=TRUE}
m16 <- glmer(correct ~ cond * block + prev_rt_z + prev_error +
              (1 + prev_rt_z + cond + prev_error | id) +
              (1 | id:block),
          na.action = na.exclude, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 30000)),
          data = flanker, family=binomial)
```

```{r}
if (isSingular(m16)) { check_singularity(m16) }
flextb_vif(m16)
flextable(car::Anova(m16, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
flextable(render_aictab(minfo=minfo, m0, m1, m2, m3, m4, m5, m6, m7, m8, m9, m10,
                        m11, m12, m13, m14, m15, m16)) %>% autofit()
```

## m15 is the winner!

```{r}
library(broom.mixed)

flextable(car::Anova(m15, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
summary(m15)

tidy(m15,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
```


```{r fplot, cache=TRUE, fig=TRUE}
library(sjPlot)
gg <- plot_model(m15, type="std", show.p=TRUE, ci.lvl=.95, dot.size=5, 
                 line.size=2, vline.color = "black", axis.lim=c(0.15, 3.5)) + 
  theme_bw(base_size=24) +
  theme(panel.grid.major.y=element_blank()) +
  ggtitle("") + ylab("Odds Ratio")
plot(gg)
ggsave(gg, filename="Flanker_Acc_Params.pdf", width=9, height=6, useDingbats=FALSE)
```
