---
title: "Final Recent Probes Accuracy Analyses"
subtitle: "PD Inhibition Project"
author: "Michael Hallquist"
date: "17 June 2020"
output: 
  html_document:
    code_folding: show
    df_print: default
    mathjax: default
    number_sections: no
    theme: spacelab
    toc: yes
    toc_depth: 2
    toc_float: no
    fig_width: 9 
    fig_height: 6 
  pdf_document:
    df_print: default
    number_sections: no
    toc: yes
    toc_depth: 4
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require(pacman)) { install.packages("pacman"); library(pacman) }
p_load(car, nlme, lme4, readr, tidyverse, emmeans, cowplot, bbmle, broom, knitr, kableExtra, flextable, stargazer, lmerTest)
knitr::opts_chunk$set(echo = TRUE) #print code by default
#knitr::opts_chunk$set(cache.path = "../../Outputs/flanker_mlms/")
#options(digits=2)
options(scipen = 2, digits = 3)
options(width = 140)
emm_options(disable.pbkrtest = TRUE, lmerTest.limit=2e4) #disable KR and estimate Satterthwaite

#preprocessed in flanker_mlm.Rmd
rp <- read.csv(file="../../../Data/preprocessed/recent_probes_full_sample_accCode.csv") %>% rename(correct = response, rt_log = rt_log_trim_grp, conflict = cond, cond = stim, id = subj_idx) 
rp <- rp %>% 
  mutate(correct = ifelse(is.na(rt_log), NA, correct),
         prev_rt=lag(rt) ,
         prev_rt = prev_rt - mean(prev_rt, na.rm=TRUE),
         prev_rt_z = as.vector(scale(prev_rt)),
         prev_error = ifelse(lag(correct) == 1, 0, 1)) #%>% #z-score rt to put parameter estimates on smaller scale
  # filter(correct==1) # & exclude < 3) %>% #least restrictive exclusions
  
  rp[1,"prev_rt"] <- rp[2,"prev_rt"]
rp[1,"prev_rt_z"] <- rp[2,"prev_rt_z"]
rp[1,"prev_error"] <- 0

render_aictab <- function(minfo, ...) {
  mc <- match.call(expand.dots = TRUE)
  mlist <- list(...)
  
  #N.B. AICtab fails if you try to assign names to the list names(mlist) <- ...
  mnames <- sapply(3:length(mc), function(x) { as.character(mc[[x]])})
  mdf <- do.call(rbind, minfo) %>% as.data.frame() %>% rownames_to_column("model")
  adf <- AICtab(mlist, sort=FALSE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE, mnames=mnames) %>% 
    as.data.frame() %>% rownames_to_column("model") %>% dplyr::select(-dLogLik)
  
  res <- mdf %>% left_join(adf, by="model")
  return(res)
}

flextb_vif <- function(m) {
  flextable(data.frame(vif=car::vif(m)) %>% rownames_to_column("Predictor")) %>% autofit()
}

check_singularity <- function(lmerobj) {
  tt <- getME(lmerobj,"theta") #RE estimates
  ll <- getME(lmerobj,"lower") #lower bound on estimate
  
  #look for RE estimates that are very small (near zero) and the lower bound encompasses 0
  low_re <- tt[ll==0 & tt < 1e-2]
  return(low_re)
  
  #eventually, would be nice to provide functionality to drop these from model and refit automatically
}

minfo <- list() #used for building model summary table
```

This file contains final MLMs for accuracy statistics on the recent probes task for the PD Inhibition DDM project.

## m1: design effects random intercept of subject

```{r}
minfo <- list() 
minfo[["m1"]] <- c(fixed="Condition", l2="Subject: Intercept")
```

```{r m1_lmer, cache=TRUE}
m1 <- glmer(correct ~ cond + (1|id),
          na.action = na.exclude, 
          data = rp, family=binomial)
```

```{r}
flextable(car::Anova(m1, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
# flextb_vif(m0)
emmeans(m1, ~cond, type = "response") %>% data.frame() %>%
    flextable() %>% autofit() %>%
    save_as_docx(path = "~/Desktop/emmeans_rp_conditions_acc.docx")
  
emm1 <- emmeans(m1, ~cond, type = "response")

pairs(emm1)
anova(m1)
summary(m1)
```
interesting that positive seems the lowest... easy to forget?

## m2: fixed condition, random condition

```{r}
# minfo <- list() 
minfo[["m2"]] <- c(fixed="Condition", l2="Subject: Intercept, Condition")
```

```{r m1_lmer, cache=TRUE}
m2 <- glmer(correct ~ cond + (1 + cond|id),
          na.action = na.exclude, 
          data = rp, family=binomial,
          control=glmerControl(optCtrl=list(maxfun=2e4)))
# beepr::beep()         
```

```{r}
flextable(car::Anova(m2, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
# flextb_vif(m0)
(emm2 <- emmeans(m2, ~cond, type="response"))
pairs(emm2)
# anova(m2)
flextable(render_aictab(minfo=minfo, m1, m2)) %>% autofit()
```


## m3: fixed condition add trial as fixed effect

```{r}
# minfo <- list() 
minfo[["m3"]] <- c(fixed="Condition, Trial", l2="Subject: Intercept")
```

```{r m3_lmer, cache=TRUE}
m3 <- glmer(correct ~ cond+ trial_z + (1 |id),
          na.action = na.exclude, 
          data = rp, family=binomial)#,
          # control=glmerControl(optCtrl=list(maxfun=2e4)))
# beepr::beep()         
```

```{r}
flextable(car::Anova(m3, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
# flextb_vif(m0)
# (emm3 <- emmeans(m3, ~cond, type="response"))
# pairs(emm3)
summary(m3)
flextable(render_aictab(minfo=minfo, m1, m2, m3)) %>% autofit()
```

## m4: fixed condition and trial, random trial

```{r}
# minfo <- list() 
minfo[["m4"]] <- c(fixed="Condition, Trial", l2="Subject: Intercept, Trial")
```

```{r m1_lmer, cache=TRUE}
m4 <- glmer(correct ~ cond + trial_z + (1 + trial_z|id),
          na.action = na.exclude, 
          data = rp, family=binomial)#,
          # control=glmerControl(optCtrl=list(maxfun=2e4)))
# beepr::beep()  


```

```{r}
summary(m4)
flextable(car::Anova(m4, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
# flextb_vif(m0)
# (emm2 <- emmeans(m2, ~cond, type="response"))
# pairs(emm2)
# anova(m2)
flextable(render_aictab(minfo=minfo, m1, m2, m3, m4)) %>% autofit()
```

## m5: fixed condition, trial, prev rt, random trial

```{r}
# minfo <- list() 
minfo[["m5"]] <- c(fixed="Condition, Trial, Previous RT", l2="Subject: Intercept, Trial")
```

```{r m1_lmer, cache=TRUE}
m5 <- glmer(correct ~ cond + trial_z + prev_rt_z + (1 + trial_z|id),
          na.action = na.exclude, 
          data = rp, family=binomial,
          control=glmerControl(optCtrl=list(maxfun=2e4)))
# beepr::beep()         
```

```{r}
summary(m5)
flextable(car::Anova(m5, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
# flextb_vif(m0)
# (emm2 <- emmeans(m2, ~cond, type="response"))
# pairs(emm2)
# anova(m2)
flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5)) %>% autofit()
flextb_vif(m5)
```

## m6: fixed condition, trial, prev rt, random trial, prev_rt

```{r}
# minfo <- list() 
minfo[["m6"]] <- c(fixed="Condition, Trial, Previous RT", l2="Subject: Intercept, Trial, Previous RT")
```

```{r m6_lmer, cache=TRUE}
m6 <- glmer(correct ~ cond + trial_z + prev_rt_z + (1 + trial_z + prev_rt_z |id),
          na.action = na.exclude, 
          data = rp, family=binomial,
          control=glmerControl(optCtrl=list(maxfun=2e4)))
# beepr::beep()         
```

```{r}
summary(m6)
flextable(car::Anova(m6, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
# flextb_vif(m0)
# (emm2 <- emmeans(m2, ~cond, type="response"))
# pairs(emm2)
# anova(m2)
flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5, m6)) %>% autofit()
```


## m7: fixed condition, trial, prev rt, prev error. random: trial

```{r}
# minfo <- list() 
minfo[["m7"]] <- c(fixed="Condition, Trial, Previous RT, Previous Error", l2="Subject: Intercept, Trial")
```

```{r m7_lmer, cache=TRUE}
m7 <- glmer(correct ~ cond + trial_z + prev_rt_z + prev_error + (1 + trial_z|id),
          na.action = na.exclude, 
          data = rp, family=binomial,
          control=glmerControl(optCtrl=list(maxfun=2e4)))
# beepr::beep()         
```

```{r}
summary(m7)
flextable(car::Anova(m7, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
# flextb_vif(m0)
# (emm2 <- emmeans(m2, ~cond, type="response"))
# pairs(emm2)
# anova(m2)
flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5, m6, m7)) %>% autofit()# %>% save_as_docx(path = "~/Desktop/rp_aictable_accuracy.docx")
```



```{r fplot, cache=TRUE, fig=TRUE}
rp$cond <- as.factor(ifelse(rp$cond == "positive", "apositive", as.character(rp$cond )))

m5 <- glmer(correct ~ cond + trial_z + prev_rt_z + (1 + trial_z|id),
          na.action = na.exclude, 
          data = rp, family=binomial,
          control=glmerControl(optCtrl=list(maxfun=2e4)))

summary(m5)
flextable(car::Anova(m5, type=3) %>% rownames_to_column("Predictor")) %>% autofit()
tidy(m5,conf.int=TRUE,exponentiate=TRUE,effects="fixed")

emm5 <- emmeans(m5, ~cond, type = "response")
pairs(emm5)
```

```{r}
library(sjPlot)
gg <- plot_model(m5, type="std", show.p=TRUE, ci.lvl=.95, dot.size=5, 
                 line.size=2, vline.color = "black", axis.lim=c(.5, 8)) + 
  theme_bw(base_size=24) +
  theme(panel.grid.major.y=element_blank()) +
  ggtitle("") + ylab("Odds Ratio")
plot(gg)
ggsave(gg, filename="Rp_Acc_Params.pdf", width=9, height=6, useDingbats=FALSE)
```
```{r}

```




## m15 as probit

To match Mplus

```{r m15_probit, cache=TRUE}
m15 <- glmer(correct ~ cond + block + prev_rt_z + prev_error +
              (1 + prev_rt_z + cond + prev_error | id) +
              (1 | id:block),
          na.action = na.exclude, control=glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 30000)),
          data = flanker, family = binomial(link = "probit"))

summary(m15)
```