---
title: "Final Recent Probes RT Analyses"
subtitle: "PD Inhibition Project"
author: "Nate Hall and Michael Hallquist"
date: "15 June 2020"
output: 
  html_document:
    code_folding: show
    df_print: default
    mathjax: default
    number_sections: no
    theme: spacelab
    toc: yes
    toc_depth: 2
    toc_float: no
    fig_width: 9 
    fig_height: 6 
  pdf_document:
    df_print: default
    number_sections: no
    toc: yes
    toc_depth: 4
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require(pacman)) { install.packages("pacman"); library(pacman) }
p_load(car, nlme, lme4, readr, tidyverse, emmeans, cowplot, bbmle, broom, knitr, kableExtra, flextable, stargazer, lmerTest)
knitr::opts_chunk$set(echo = TRUE) #print code by default
#knitr::opts_chunk$set(cache.path = "../../Outputs/flanker_mlms/")
#options(digits=2)
options(scipen = 2, digits = 3)
options(width = 140)
emm_options(disable.pbkrtest = TRUE, lmerTest.limit=2e4) #disable KR and estimate Satterthwaite

##MNH: You need to group_by subject by lagging to avoid copying the first RT of one subject as the last RT of the previous

#preprocessed in flanker_mlm.Rmd
rp <- read.csv(file="../../../Data/preprocessed/recent_probes_full_sample_accCode.csv") %>% 
  rename(correct = response, rt_log = rt_log_trim_grp, conflict = cond, cond = stim, id = subj_idx) %>%
  mutate(
    correct = if_else(is.na(rt_log), NA_integer_, correct),
    error = 1-correct
  ) %>% group_by(id) %>%
  mutate(
    prev_rt=dplyr::lag(rt, 1, order_by=trial),
    prev_rt_wicent = prev_rt - mean(prev_rt, na.rm=TRUE), #within-person centering
    prev_error=dplyr::lag(error, 1, order_by=trial),
    prev_cond=dplyr::lag(cond, 1, order_by=trial)
  ) %>% ungroup() %>%
  mutate(
    prev_rt_z = as.vector(scale(prev_rt))
  )
  
#sanity checks
xtabs(~trial + id, rp)
xtabs(~cond + id, rp)
xtabs(~correct + id, rp)

#only keep RTs for correct trials
rp <- rp %>% filter(correct==1)

#MNH: for the prev_rt models to be commensurable to models lacking that predictor, we need to drop all rows with a missing prev_rt.
rp <- rp %>% filter(!is.na(prev_rt))

render_aictab <- function(minfo, ...) {
  mc <- match.call(expand.dots = TRUE)
  mlist <- list(...)
  
  #N.B. AICtab fails if you try to assign names to the list names(mlist) <- ...
  mnames <- sapply(3:length(mc), function(x) { as.character(mc[[x]])})
  mdf <- do.call(rbind, minfo) %>% as.data.frame() %>% rownames_to_column("model")
  adf <- AICtab(mlist, sort=FALSE, delta=TRUE, weights=TRUE, logLik=TRUE, base=TRUE, mnames=mnames) %>% 
    as.data.frame() %>% rownames_to_column("model") %>% dplyr::select(-dLogLik)
  
  res <- mdf %>% left_join(adf, by="model")
  return(res)
}

flextb_vif <- function(m) {
  flextable(data.frame(vif=car::vif(m)) %>% rownames_to_column("Predictor")) %>% autofit()
}

check_singularity <- function(lmerobj) {
  tt <- getME(lmerobj,"theta") #RE estimates
  ll <- getME(lmerobj,"lower") #lower bound on estimate
  
  #look for RE estimates that are very small (near zero) and the lower bound encompasses 0
  low_re <- tt[ll==0 & tt < 1e-2]
  return(low_re)
  
  #eventually, would be nice to provide functionality to drop these from model and refit automatically
}

minfo <- list() #used for building model summary table
```

This will be a simple extension of Michael's code from flanker analyses. I will skip the lme approach for consistency across modelling efforts.

Guidance from Michael on prior flanker modelling efforts below: 


This file contains final MLMs for reaction times on the flanker task for the PD Inhibition DDM project.

Note: I have adopted the common convention of only analyzing RTs for correct responses. This assumes that whatever process gives rise to the RT for an incorrect response is not commensurable. The alternative would be to allow for `correct` to enter into the model as a predict of the current trial's RT. This could support moderation analyses -- for example, whether error RTs are faster in the mostly congruent condition for incongruent trials. The downside is all of the ensuing multi-way interactions, many of which are not of central interest.

N.B. For the AIC comparisons to be valid, we need to use method='ML' throughout. Once we have a winning model,
or one where the parameters matter, re-estimate with REML. `update(mm, method='REML')`

To reduce the number of models, I don't consider block diagonal matrices for L2 random effects. This is achieved with `pdDiag()` and basically estimates a unique variance component for each level of a factor. But the fits of these models are extremely close to the more conventional block within id `id/block` parameterization for random effects. Given that the latter is much more conventional, let's stick with that when we want to check for heterogeneity in L2 by condition.


# LMER-based modeling

## m1: stimulus effect, random intercept of subject

```{r}
minfo <- list() #re-initialize now that we're eliminating l1 heterogeneity
```

```{r m1_lmer, cache=TRUE}
minfo[["m1"]] <- c(fixed="Condition", l2="Subject: Intercept")
m1 <- lmer(rt_log ~ cond + (1|id),
           na.action = na.exclude, 
           data = rp, REML=FALSE)
m1_reml <- update(m1, REML=TRUE)
```

```{r}
flextable(anova(m1) %>% rownames_to_column("Effect")) %>% autofit() #lmerTest reports Satterthwaite degrees of freedom
#flextable(car::Anova(m1, type=3)) %>% autofit()

#Get model-predicted means in original RT scale. Force back onto original RT using custom function
rg <- update(ref_grid(m1_reml),  tran=list(linkinv=function(x) { (10^x)}, mu.eta=function(x) { 10^(x)}),predict.type="response")   #N.B. we used log10, so use 10^ rather than exp()
res_trans <- emmeans(rg, ~cond, lmer.df = "satterthwaite") #this seems off, but consult with MH

# emmeans(m1_reml, ~cond|block, lmer.df = "satterthwaite") #in inverse units

flextable(as.data.frame(res_trans)) %>% 
  colformat_num(j=c("response", "SE", "lower.CL", "upper.CL"), digits=2) %>% 
  autofit() %>% save_as_docx(path = "~/Desktop/emmeans_rp_conditions.docx")

```


## m2: conflict effect, random intercept of subject

```{r m2_lmer, cache=TRUE}
minfo[["m2"]] <- c(fixed="Conflict", l2="Subject: Intercept")
m2 <- lmer(rt_log ~ conflict + (1|id),
           na.action = na.exclude, 
           data = rp, REML=FALSE)
m2_reml <- update(m1, REML=TRUE)
```

```{r}
flextable(anova(m2) %>% rownames_to_column("Effect")) %>% autofit() #lmerTest reports Satterthwaite degrees of freedom
#flextable(car::Anova(m1, type=3)) %>% autofit()

#Get model-predicted means in original RT scale. Force back onto original RT using custom function
rg <- update(ref_grid(m2_reml), tran=list(linkinv=function(x) { log(x) }, mu.eta=function(x) { log(x) }), predict.type="response")
res_trans <- emmeans(rg, ~cond, lmer.df = "satterthwaite")

# emmeans(m1_reml, ~cond|block, lmer.df = "satterthwaite") #in inverse units

flextable(as.data.frame(res_trans)) %>% 
  colformat_num(j=c("response", "SE", "lower.CL", "upper.CL"), digits=2) %>% 
  autofit()

```

## m3: Add condition as random slopes within subject

```{r m3_lmer, cache=TRUE}
minfo[["m3"]] <- c(fixed="Condition", l2="Subject: Intercept, Condition")
m3 <- lmer(rt_log ~ cond + (1 + cond| id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
```

## m4: Add condition and conflict as fixed: after fitting, these models are rank-deficient, since they are pretty much the same thing. Fall back on condition only.

## m4: add trial as fixed effect

```{r m4_lmer, cache=TRUE}
minfo[["m4"]] <- c(fixed="Condition,  Trial", l2="Subject: Intercept")
m4 <- lmer(rt_log ~ cond  + trial_z + (1 | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
```


## m5: Add trial_z as random slopes within subject

```{r m5_lmer, cache=TRUE}
minfo[["m5"]] <- c(fixed="Condition,  Trial", l2="Subject: Intercept, Trial")
m5 <- lmer(rt_log ~ cond  + trial_z + (1 + trial_z| id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
```



```{r}
flextable(render_aictab(minfo=minfo, m1, m2, m3,m4,m5)) %>% autofit()
```

## m6: Add prev_rt as fixed

MNH: converges okay for me

```{r m6_lmer, cache=TRUE}
minfo[["m6"]] <- c(fixed="Condition,  Trial, Previous RT", l2="Subject:Intercept, Trial")
m6 <- lmer(rt_log ~ cond + trial_z + prev_rt_z +  (1 + trial_z| id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
```

## m7: Add prev_rt as random

```{r m7_lmer, cache=TRUE}
minfo[["m7"]] <- c(fixed="Condition,  Trial, Previous RT", l2="Subject:Intercept, Trial, Previous RT")
m7 <- lmer(rt_log ~ cond  + trial_z + prev_rt_z +  (1 + trial_z + prev_rt_z | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
```

## m=8: Remove prev_rt as fixed

```{r m8_lmer, cache=TRUE}
minfo[["m8"]] <- c(fixed="Condition,  Trial", l2="Subject:Intercept, Trial, Previous RT")
m8 <- lmer(rt_log ~ cond  + trial_z  +  (1 + trial_z + prev_rt_z | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
```

```{r}

flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5,m6, m7, m8)) %>% autofit()
```

## m9: add prev_error as fixed

```{r m9_lmer, cache=TRUE}
minfo[["m9"]] <- c(fixed="Condition,  Trial, Previous Error", l2="Subject:Intercept, Trial")
m9 <- lmer(rt_log ~ cond  + trial_z + prev_error +  (1 + trial_z  | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
flextb_vif(m9)
summary(m9)
```

## m10: add prev_error as random

```{r m10_lmer, cache=TRUE}
minfo[["m10"]] <- c(fixed="Condition,  Trial, Previous Error", l2="Subject:Intercept, Trial, Previous Error")
m10 <- lmer(rt_log ~ cond  + trial_z + prev_error +  (1 + trial_z +prev_error | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
# flextb_vif(m9)
# summary(m9)
```

## m11: remove prev_error as fixed effect

```{r m11_lmer, cache=TRUE}
minfo[["m11"]] <- c(fixed="Condition,  Trial", l2="Subject:Intercept, Trial, Previous Error")
m11 <- lmer(rt_log ~ cond  + trial_z +  (1 + trial_z + prev_error | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
# flextb_vif(m10)
anova(m11)
summary(m11)

```

```{r}

flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5,m6, m7, m8, m9, m10, m11)) %>% autofit() %>% save_as_docx(path = "~/Desktop/aictable_rp_rt.docx")
```

## m12: allow trial and Condition to interact at fixed level

Ugly vifs for trial x cond interaction

```{r m12_lmer, cache=TRUE}
minfo[["m12"]] <- c(fixed="Condition,  Trial, Condition x Trial", l2="Subject:Intercept, Trial")
m12 <- lmer(rt_log ~ cond*trial_z + (1 + trial_z | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
flextb_vif(m12)
# summary(m10)
```

## m13: allow previous RT and Condition to interact at fixed level
```{r m13_lmer, cache=TRUE}
minfo[["m13"]] <- c(fixed="Condition,  Trial, Condition x Previous RT", l2="Subject:Intercept, Trial")
m13 <- lmer(rt_log ~ cond*prev_rt_z  + trial_z +  (1 + trial_z | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
flextb_vif(m13)
```

## m14: allow previous error and Condition to interact at fixed level

```{r m14_lmer, cache=TRUE}
minfo[["m14"]] <- c(fixed="Condition,  Trial, Condition x Previous Error", l2="Subject:Intercept, Trial")
m14 <- lmer(rt_log ~ cond*prev_error+ trial_z +  (1 + trial_z | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)
flextb_vif(m14)
```

## m15: allow previous condition effect

```{r, m15_lmer, cache=TRUE, fig=TRUE}
minfo[["m15"]] <- c(fixed="Condition, Trial, Previous RT, Previous Condition", l2="Subject: Intercept, Trial")
m15 <- lmer(rt_log ~ cond + trial_z + prev_rt_z + prev_cond + (1 + trial_z| id),
           na.action = na.exclude,
           data = rp, REML=FALSE)

flextb_vif(m15)
plot(emmeans(m15, ~prev_cond))
```

It looks like there is a tendency for RTs after negative familiar trials to be slower, while the other four conditions don't show much separation. Test a simple negative unfamiliar versus other contrast.

## m16: treat prev cond effects as neg familiar vs. other

```{r m16_lmer, cache=TRUE}
minfo[["m16"]] <- c(fixed="Condition, Trial, Previous RT, Previous Neg Familiar", l2="Subject: Intercept, Trial")
rp$prev_negfam <- as.numeric(rp$prev_cond=="negative_familiar")
m16 <- lmer(rt_log ~ cond + trial_z + prev_rt_z + prev_negfam + (1 + trial_z| id),
           na.action = na.exclude,
           data = rp, REML=FALSE)

flextb_vif(m16)
plot(emmeans(m16, ~prev_negfam))
```

## m17: check for any other random effects

```{r m17_lmer, cache=TRUE}
minfo[["m17"]] <- c(fixed="Condition, Trial, Previous RT, Previous Neg Familiar", l2="Subject: Intercept, Trial, a bunch")
m17 <- lmer(rt_log ~ cond + trial_z + prev_rt_z + prev_negfam + (1 + trial_z + prev_negfam + cond | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)

flextb_vif(m17)
plot(emmeans(m17, ~prev_negfam))
```
Yeah, that's over-specified. But the positive condition seems to have some variance to it...

## m18: re for positive vs. other only
```{r m18_lmer, cache=TRUE}
minfo[["m18"]] <- c(fixed="Condition, Trial, Previous RT, Previous Neg Familiar", l2="Subject: Intercept, Trial, Condpos")
rp$condpos=as.numeric(rp$cond=="positive")
m18 <- lmer(rt_log ~ cond + trial_z + prev_rt_z + prev_negfam + (1 + trial_z + condpos | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)

flextb_vif(m18)

```

## m19: add re for negfam, too
```{r m19_lmer, cache=TRUE}
minfo[["m19"]] <- c(fixed="Condition, Trial, Previous RT, Previous Neg Familiar", l2="Subject: Intercept, Trial, Negfam, Condpos")
rp$condpos=as.numeric(rp$cond=="positive")
m19 <- lmer(rt_log ~ cond + trial_z + prev_rt_z + prev_negfam + (1 + trial_z + prev_negfam + condpos | id),
           na.action = na.exclude,
           data = rp, REML=FALSE)

flextb_vif(m19)

```


```{r}

flextable(render_aictab(minfo=minfo, m1, m2, m3, m4, m5,m6, m7, m8, m9, m10, m11, m12, m13, m14, m15, m16, m17, m18, m19)) %>% autofit()
```
```{r recode_condition}

rp <- rp %>% mutate(cond = ifelse(cond == "positive", "apositive", as.character(cond)))

rp$cond <- as.factor(rp$cond)

minfo[["m5"]] <- c(fixed="Condition,  Trial", l2="Subject: Intercept, Trial")
m5 <- lmer(rt_log ~ cond  + trial_z + (1 + trial_z| id),
           na.action = na.exclude,
           data = rp, REML=FALSE)

summary(m5)
anova(m5, type = 3)

em5 <- emmeans(m5, ~cond)

pairs(pairs(em5))
```



```{r fplot, cache=TRUE, fig=TRUE}
pacman::p_load(sjPlot)
gg <- plot_model(m5, type="std", show.p=TRUE, ci.lvl=.95, dot.size=5, line.size=2) + 
  ylim(-0.1, 0.5) + theme_bw(base_size=18) +
  geom_hline(yintercept = 0, size=1.2) + 
  theme(panel.grid.major.y=element_blank()) +
  ggtitle("") + ylab("Standardized regression coefficient")
plot(gg)
#ggsave(gg, filename="~/github_repos/PD_Inhibition_DDM/Code/mlm/Recent_Probes_RT_Params.pdf", width=9, height=9, useDingbats=FALSE)
```

get model statistics to write-up
```{r, eval=FALSE}

anova()

```

